---
title: "Mania_Modelling"
author: "by_Jasmin_Doenicke"
date: "Step1"
output:
  html_document:
    toc: yes
    theme: united
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---




# STARTER CODE

```{r, warning=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

Open Libraries
```{r, echo = T, results = 'hide'}
library(ggplot2)
library(psych)
library(readr)
library(dplyr)
library(tidyr)
library(tidyverse)
```





# Load Mania data
10-ItemMania-Scale from GBI => pgbi_p_ss_score (Mania)
```{r warning=FALSE, include = FALSE}
setwd("E:/release_5.1/core/mental-health")
mh_p_gbi <- read_csv("mh_p_gbi.csv")
```

```{r, warning=FALSE}
setwd("E:/release_5.1/core/mental-health")
mh_p_gbi <- read_csv("mh_p_gbi.csv")
mh_p_gbi$eventname <- as.factor(mh_p_gbi$eventname)

# find out all categories
unique(mh_p_gbi$eventname)
```
There is data at baseline, and at 1/2/3/4-year follow up.

```{r, warning=FALSE}
mh_p_gbi$eventname <- factor(mh_p_gbi$eventname, levels = c("baseline_year_1_arm_1", "1_year_follow_up_y_arm_1", "2_year_follow_up_y_arm_1", "3_year_follow_up_y_arm_1", "4_year_follow_up_y_arm_1")) 

#create a nummerical variable with all measurement timepoints taken from the "eventname" factor
mh_p_gbi$timepoint <- mh_p_gbi$eventname
mh_p_gbi <- mh_p_gbi %>% mutate(timepoint=recode(timepoint,
                                "baseline_year_1_arm_1" = "0",
                                "1_year_follow_up_y_arm_1" = "1",
                                "2_year_follow_up_y_arm_1" = "2",
                                "3_year_follow_up_y_arm_1" = "3",
                                "4_year_follow_up_y_arm_1" = "4"))
mh_p_gbi$timepoint <- as.numeric(mh_p_gbi$timepoint)

table(mh_p_gbi$eventname)
```
However, the data at the 3-year and 4-year follow up seems to be incomplete! Let's have a closer look by plotting the data next.

```{r, warning=FALSE}
#Plot mean
library(ggplot2)
ggplot(mh_p_gbi, aes(timepoint, pgbi_p_ss_score)) + 
  geom_jitter(width = 0.3, height = 0, size = 0.5)+
  ylab("Mania_Score")+
  xlab("Point of Measurement")+ 
  stat_summary(fun = mean, geom = "point", size = 2, col = "red")  +
  ggtitle("10-item Mania Scale (from Parent General Behavior Inventory) - Parent") +
  theme_light()
```

The distribution and mean are similar across measurements. 

```{r, warning=FALSE}
# Count how many in each event! 
mh_p_gbi %>% count(eventname)
mh_p_gbi %>% filter(!is.na(pgbi_p_ss_score)) %>% count(eventname)
```

After removing the NAs, there is clearly only usable data in baseline, follow-up 1, and follow-up2!

```{r, warning=FALSE}
data_GBI = mh_p_gbi

# save data
#save(data_GBI,file="E:/data/20240506_dataGBI.rdata")
```

The saved, cleaned data will get saved in the "data" folder, so we can continue working with it!


# Alternative Mania measures


