---
title: "Mania_Modelling"
author: "by_Jasmin_Doenicke"
date: "Step 3"
output:
  html_document:
    toc: yes
    theme: united
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---

This document prepares our data for the first calculation in Mplus.
Currently, there is: 1. the mania dataset 2. the demographics dataset. 
All necessary variables are obtained. Now, shaping it up for it to run in Mplus is necessary.

# STARTER CODE
```{r, warning=FALSE}
knitr::opts_chunk$set(error = TRUE)

# libraries
library(tidyverse)

# set working directory
setwd("F:")
```

```{r, warning=FALSE}
#load data
load(file='E:/data/GBI_demographics.rdata')

# rename dataset to "data" for cleaner code
data = GBI_demographics
```

# Data Cleaning
```{r, warning=FALSE}
# only keep the first 4 time-points (baseline, 1,2 yr follow-up)
data<-data %>% filter(!c(visit==3 |visit==4))

#filter out those with missing mania data
data <- data %>% filter(!is.na(pgbi_p_ss_score)) 

#only keep participants with 3x time points (not missing for any time-points)
data4<-data %>% group_by(src_subject_id) %>% 
  mutate(count=n()) %>% 
  filter(count==3) %>% ungroup() %>%
  select(!c(eventname,count))

#count total n participants
data4 %>% distinct(src_subject_id) %>% count() #10634
```

# Select Variables 
```{r, warning=FALSE}
#select variables we want to model 
data4<-data4 %>% select(src_subject_id,visit,site,
                        acs_raked_propensity_score,
                        pgbi_p_ss_score)

#convert to wide format
data_wide<-data4 %>% pivot_wider(
  id_cols=c(src_subject_id),
  names_from = visit,
  values_from = c(site,acs_raked_propensity_score,pgbi_p_ss_score))

#rearrange variables
data_wide<-data_wide %>% select(src_subject_id,site_0,acs_raked_propensity_score_0,
                                starts_with("pgbi"))
                          

#check missingness on acs variable
data_wide %>% filter(is.na(acs_raked_propensity_score_0)) #0 cases

#remove these participants if becessary (not the case here)
#data_wide <- data_wide %>% filter(!is.na(acs_raked_propensity_score_0))

#check final N
data4 %>% distinct(src_subject_id) %>% count() #10634

#replace missing with -99 (required for Mplus to work)
data_final<-data_wide %>% replace(is.na(.),-99)
```

# Save Data for Mplus
```{r, warning=FALSE}
##save data (id's included)
#write.csv(data_final, file='../code/MPLUS/data_headers.csv',row.names = F)

##save data (id's and headers removed)
#data_final <- data_final %>% select(-src_subject_id)
#write.csv(data_final, file='../code/MPLUS/data_noheaders.csv',row.names = F,col.names=F)
```

The data with IDs is used to keep track of what is in the data. 
The data with headers removed is used in Mplus in the next step.
