---
title: "Mania_Modelling"
author: "by_Jasmin_Doenicke"
date: "Step 4"
output:
  html_document:
    toc: yes
    theme: united
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---


Run Mplus before running this code! 
You may consult the "ReadMe" for detailed Mplus instructions.

# STARTER CODE
```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

```{r}
library(tidyverse)
library(MplusAutomation)

setwd("E:")

#load data
load(file='E:/data/GBI_demographics.rdata')
#read id's from input csv
data_csv<-read.csv('E:/code/MPLUS/data_headers.csv',
                   header=T)

##Set theme
theme_set(theme_bw())
```

# Plot MPlus Models
## NEGATIVE BINOMIAL
### Linear 1-Class
```{r}
mplus2<-readModels('E:/code/MPLUS/neg_binomial/00_linear_1class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Quadratic 1-Class
```{r}
mplus2<-readModels('E:/code/MPLUS/neg_binomial/00_quadratic_1_class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Linear 2-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/neg_binomial/01_linear_2class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Quadratic 2-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/neg_binomial/02_quadratic_2_class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Linear 3-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/neg_binomial/03_linear_3class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='3') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Quadratic 3-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/neg_binomial/04_quadratic_3_class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='3') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Linear 4-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/neg_binomial/05_linear_4class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#NEW CODE: change the order of the classes to match the quadratic model. Use this code if you need to.
merge<-merge %>% mutate(class=case_when(class==1~3, #means 'when class_l=1, change it to …'.
                                            class==2~4,#means 'when class_l=2, change it to …'.
                                            class==3~2,
                                            class==4~1))
#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='3') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
  #class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='4') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```


### Quadratic 4-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/neg_binomial/06_quadratic_4_class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)


#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='3') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class4
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='4') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Linear 5-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/neg_binomial/07_linear_5class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

## NEW: change class order 

merge<-merge %>% mutate(class=case_when(class==1~1, #means 'when class_l=1, change it to …'.
                                            class==2~3,#means 'when class_l=2, change it to …'.
                                            class==3~2,
                                            class==4~5, 
                                            class==5~4))


#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='3') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class4
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='4') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class5
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='5') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Quadratic 5-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/neg_binomial/08_quadratic_5_class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

### NEW: Change class order
merge<-merge %>% mutate(class=case_when(class==1~4, #means 'when class_l=1, change it to …'.
                                            class==2~2,#means 'when class_l=2, change it to …'.
                                            class==3~5,
                                            class==4~1, 
                                            class==5~3))
#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='3') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class4
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='4') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class5
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='5') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Linear 6-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/neg_binomial/09_linear_6_class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='3') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class4
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='4') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
  #class5
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='5') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class6
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='6') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Quadratic 6-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/neg_binomial/10_quadratic_6_class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='3') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class4
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='4') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class5
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='5') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class6
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='6') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

## POISSON
### Linear 1-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/poisson/00_linear_1class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Quadratic 1-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/poisson/00_quadratic_1_class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Linear 2-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/poisson/01_linear_2class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Quadratic 2-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/poisson/02_quadratic_2_class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Linear 3-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/poisson/03_linear_3class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='3') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Quadratic 3-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/poisson/04_quadratic_3_class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='3') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Linear 4-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/poisson/05_linear_4class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='3') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
  #class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='4') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```


### Quadratic 4-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/poisson/06_quadratic_4_class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='3') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class4
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='4') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Linear 5-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/poisson/07_linear_5class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='3') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class4
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='4') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class5
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='5') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Quadratic 5-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/poisson/08_quadratic_5_class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='3') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class4
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='4') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class5
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='5') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Linear 6-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/poisson/09_linear_6class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='3') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class4
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='4') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
  #class5
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='5') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class6
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='6') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 1), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```

### Quadratic 6-Class
```{r}

mplus2<-readModels('E:/code/MPLUS/poisson/10_quadratic_6_class.out',
                  what=c("savedata"))$savedata

#merge all data
mplus2merge<-cbind(data_csv,mplus2)
mplus2merge<-mplus2merge %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,mplus2merge)

#plot all classes
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot with individual lines
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.1)+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))

#plot individuals per group
#class1
merge %>%
  mutate(class=factor(class)) %>%
  filter(!c(visit=="3"|visit=="4")) %>%
  filter(class=='1') %>%
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey60')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
#class2
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='2') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class3
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='3') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class4
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='4') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class5
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='5') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
  
#class6
  merge %>%
  mutate(class=factor(class)) %>%
    filter(!c(visit=="3"|visit=="4")) %>%
    filter(class=='6') %>%                # Change class here (ex. 2)
  ggplot(aes(y=pgbi_p_ss_score,x=visit,color=class,fill=class))+
  #geom_point()+
  geom_line(aes(group=src_subject_id),alpha=0.2,color='grey80')+
  geom_smooth(method="lm",formula=y ~ poly(x, 2), # quadratic: (x,2); linear: (x,1)
              aes(group=class))
```


