---
title: "Mania_Modelling"
author: "by_Jasmin_Doenicke"
date: "Step 5"
output:
  html_document:
    toc: yes
    theme: united
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

Previously, I explored potential mania trajectories in the dataset, identifying between 1 to 6 possible groups with varying distributions. The plots in Step 4 illustrate all these options—but which model is the best fit? To determine this, I will examine the results and fit statistics. Please have a look at "05_model_comparison_table_05.pdf" for the results!

# STARTER CODE
```{r, error=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

```{r, error=FALSE}
library(tidyverse)
library(MplusAutomation)
library(tidyr)
library(dplyr)
library(stringr)

setwd("E:")

#load data
load(file='E:/data/GBI_demographics.rdata')
#read id's from input csv
data_csv<-read.csv('E:/code/MPLUS/data_headers.csv',
                   header=T)

##Set theme
theme_set(theme_bw())
```


# Negative Binomial

Let's read in results from the latent analysis from Mplus using the readModels() function from the MplusAutomation package in R.

## Read In Models

Firstly, let's read in the model summaries. This retrieves fit indices (e.g., AIC, BIC, entropy, log-likelihood) for different models. This helps in model comparison to determine the best number of classes.


```{r, error=FALSE}
# 1-Class
m1_nb_l <-readModels('E:/code/MPLUS/neg_binomial/00_linear_1class.out',
                  what=c("summaries"))$summaries
m1_nb_q <-readModels('E:/code/MPLUS/neg_binomial/00_quadratic_1class.out',
                  what=c("summaries"))$summaries

# 2-Class
m2_nb_l <-readModels('E:/code/MPLUS/neg_binomial/01_linear_2class.out',
                  what=c("summaries"))$summaries
m2_nb_q <-readModels('E:/code/MPLUS/neg_binomial/01_quadratic_2class.out',
                  what=c("summaries"))$summaries

# 3-Class
m3_nb_l <-readModels('E:/code/MPLUS/neg_binomial/02_linear_3class.out',
                  what=c("summaries"))$summaries
m3_nb_q <-readModels('E:/code/MPLUS/neg_binomial/02_quadratic_3class.out',
                  what=c("summaries"))$summaries

# 4-Class
m4_nb_l <-readModels('E:/code/MPLUS/neg_binomial/03_linear_4class.out',
                  what=c("summaries"))$summaries
m4_nb_q <-readModels('E:/code/MPLUS/neg_binomial/03_quadratic_4class.out',
                  what=c("summaries"))$summaries

# 5-Class
m5_nb_l <-readModels('E:/code/MPLUS/neg_binomial/04_linear_5class.out',
                  what=c("summaries"))$summaries
m5_nb_q <-readModels('E:/code/MPLUS/neg_binomial/04_quadratic_5class.out',
                  what=c("summaries"))$summaries

# 6-Class
m6_nb_l <-readModels('E:/code/MPLUS/neg_binomial/05_linear_6class.out',
                  what=c("summaries"))$summaries
m6_nb_q <-readModels('E:/code/MPLUS/neg_binomial/05_quadratic_6class.out',
                  what=c("summaries"))$summaries
```

## Read in Classes 

Secondly, let's read in the class counts. This extracts the number of individuals assigned to each latent class and helps assess class sizes and interpretability of solutions.

```{r, error=FALSE}
# 1-Class
class_m1_nb_l <-readModels('E:/code/MPLUS/neg_binomial/00_linear_1class.out',
                        what=c("class_counts"))$class_counts
class_m1_nb_q <-readModels('E:/code/MPLUS/neg_binomial/00_quadratic_1class.out',
                        what=c("class_counts"))$class_counts

# 2-Class
class_m2_nb_l <-readModels('E:/code/MPLUS/neg_binomial/01_linear_2class.out',
                        what=c("class_counts"))$class_counts
class_m2_nb_q <-readModels('E:/code/MPLUS/neg_binomial/01_quadratic_2class.out',
                        what=c("class_counts"))$class_counts

# 3-Class
class_m3_nb_l <-readModels('E:/code/MPLUS/neg_binomial/02_linear_3class.out',
                        what=c("class_counts"))$class_counts
class_m3_nb_q <-readModels('E:/code/MPLUS/neg_binomial/02_quadratic_3class.out',
                        what=c("class_counts"))$class_counts

# 4-Class
class_m4_nb_l <-readModels('E:/code/MPLUS/neg_binomial/03_linear_4class.out',
                        what=c("class_counts"))$class_counts
class_m4_nb_q <-readModels('E:/code/MPLUS/neg_binomial/03_quadratic_4class.out',
                        what=c("class_counts"))$class_counts

# 5-Class
class_m5_nb_l <-readModels('E:/code/MPLUS/neg_binomial/04_linear_5class.out',
                        what=c("class_counts"))$class_counts
class_m5_nb_q <-readModels('E:/code/MPLUS/neg_binomial/04_quadratic_5class.out',
                        what=c("class_counts"))$class_counts

# 6-Class
class_m6_nb_l <-readModels('E:/code/MPLUS/neg_binomial/05_linear_6class.out',
                        what=c("class_counts"))$class_counts
class_m6_nb_q <-readModels('E:/code/MPLUS/neg_binomial/05_quadratic_6class.out',
                        what=c("class_counts"))$class_counts
```


# Poisson
## Read in models

Firstly, let's read in the model summaries. This retrieves fit indices (e.g., AIC, BIC, entropy, log-likelihood) for different models. This helps in model comparison to determine the best number of classes.

```{r, error=FALSE}
# 1-Class
m1_p_l <-readModels('E:/code/MPLUS/poisson/00_linear_1class.out',
                  what=c("summaries"))$summaries
m1_p_q <-readModels('E:/code/MPLUS/poisson/00_quadratic_1class.out',
                  what=c("summaries"))$summaries

# 2-Class
m2_p_l <-readModels('E:/code/MPLUS/poisson/01_linear_2class.out',
                  what=c("summaries"))$summaries
m2_p_q <-readModels('E:/code/MPLUS/poisson/01_quadratic_2class.out',
                  what=c("summaries"))$summaries

# 3-Class
m3_p_l <-readModels('E:/code/MPLUS/poisson/02_linear_3class.out',
                  what=c("summaries"))$summaries
m3_p_q <-readModels('E:/code/MPLUS/poisson/02_quadratic_3class.out',
                  what=c("summaries"))$summaries

# 4-Class
m4_p_l <-readModels('E:/code/MPLUS/poisson/03_linear_4class.out',
                  what=c("summaries"))$summaries
m4_p_q <-readModels('E:/code/MPLUS/poisson/03_quadratic_4class.out',
                  what=c("summaries"))$summaries

# 5-Class
m5_p_l <-readModels('E:/code/MPLUS/poisson/04_linear_5class.out',
                  what=c("summaries"))$summaries
m5_p_q <-readModels('E:/code/MPLUS/poisson/04_quadratic_5class.out',
                  what=c("summaries"))$summaries

# 6-Class
m6_p_l <-readModels('E:/code/MPLUS/poisson/05_linear_6class.out',
                  what=c("summaries"))$summaries
m6_p_q <-readModels('E:/code/MPLUS/poisson/05_quadratic_6class.out',
                  what=c("summaries"))$summaries
```

## Read in Classes

Secondly, let's read in the class counts. This extracts the number of individuals assigned to each latent class and helps assess class sizes and interpretability of solutions.

```{r, error=FALSE}
# 1-Class
class_m1_p_l <-readModels('E:/code/MPLUS/poisson/00_linear_1class.out',
                        what=c("class_counts"))$class_counts
class_m1_p_q <-readModels('E:/code/MPLUS/poisson/00_quadratic_1class.out',
                        what=c("class_counts"))$class_counts

# 2-Class
class_m2_p_l <-readModels('E:/code/MPLUS/poisson/01_linear_2class.out',
                        what=c("class_counts"))$class_counts
class_m2_p_q <-readModels('E:/code/MPLUS/poisson/01_quadratic_2class.out',
                        what=c("class_counts"))$class_counts

# 3-Class
class_m3_p_l <-readModels('E:/code/MPLUS/poisson/02_linear_3class.out',
                        what=c("class_counts"))$class_counts
class_m3_p_q <-readModels('E:/code/MPLUS/poisson/02_quadratic_3class.out',
                        what=c("class_counts"))$class_counts

# 4-Class
class_m4_p_l <-readModels('E:/code/MPLUS/poisson/03_linear_4class.out',
                        what=c("class_counts"))$class_counts
class_m4_p_q <-readModels('E:/code/MPLUS/poisson/03_quadratic_4class.out',
                        what=c("class_counts"))$class_counts

# 5-Class
class_m5_p_l <-readModels('E:/code/MPLUS/poisson/04_linear_5class.out',
                        what=c("class_counts"))$class_counts
class_m5_p_q <-readModels('E:/code/MPLUS/poisson/04_quadratic_5class.out',
                        what=c("class_counts"))$class_counts

# 6-Class
class_m6_p_l <-readModels('E:/code/MPLUS/poisson/05_linear_6class.out',
                        what=c("class_counts"))$class_counts
class_m6_p_q <-readModels('E:/code/MPLUS/poisson/05_quadratic_6class.out',
                        what=c("class_counts"))$class_counts
```

# Summarize Model Results

This organizes and processes model summary results from models using Poisson (P) and Negative Binomial (NB) distributions.

```{r, error=FALSE}
colnames(m1_nb_l)
colnames(m2_nb_l)
colnames(m3_p_q)

# fixing m3_p_q
m3_p_q = m3_p_q %>% mutate(T11_VLMR_Mean = 1, T11_VLMR_SD = 1)
                           
# 1-Class Models separate
sums_1Class<-rbind(m1_nb_l, m1_nb_q, m1_p_l, m1_p_q) %>% select(Filename,Parameters,AIC,BIC,aBIC) %>% mutate(model = c("NB_Linear", "NB_Quadratic", "P_Linear", "P_Quadratic"))

# All 2 to 6 class models
sums<-rbind(m2_nb_l, m2_nb_q, m3_nb_l, m3_nb_q, m4_nb_l, m4_nb_q, m5_nb_l, m5_nb_q, m6_nb_l, m6_nb_q, m2_p_l, m2_p_q, m3_p_l, m3_p_q, m4_p_l, m4_p_q, m5_p_l, m5_p_q, m6_p_l, m6_p_q) %>%  select(Filename,Parameters,AIC,BIC,aBIC,Entropy,T11_VLMR_PValue,T11_LMR_PValue) %>% mutate(model = c("NB","NB", "NB", "NB", "NB", "NB", "NB", "NB", "NB", "NB", "P", "P", "P", "P", "P", "P", "P", "P", "P", "P" ))

# Linear Poisson
sums_Linear_P<-rbind(m2_p_l, m3_p_l, m4_p_l, m5_p_l, m6_p_l) %>%  select(Filename,Parameters,AIC,BIC,aBIC,Entropy,T11_VLMR_PValue,T11_LMR_PValue)

# Linear Negative Binomial
sums_Linear_NB<-rbind(m2_nb_l, m3_nb_l, m4_nb_l, m5_nb_l, m6_nb_l) %>%  select(Filename,Parameters,AIC,BIC,aBIC,Entropy,T11_VLMR_PValue,T11_LMR_PValue) 

# Quadratic Poisson
sums_Quadratic_P <-rbind(m2_p_q, m3_p_q, m4_p_q, m5_p_q, m6_p_q) %>%  select(Filename,Parameters,AIC,BIC,aBIC,Entropy,T11_VLMR_PValue,T11_LMR_PValue) 

# Quadratic Negative Binomial
sums_Quadratic_NB <-rbind(m2_nb_q, m3_nb_q, m4_nb_q, m5_nb_q, m6_nb_q) %>%  select(Filename,Parameters,AIC,BIC,aBIC,Entropy,T11_VLMR_PValue,T11_LMR_PValue)
```


```{r, error=FALSE}
#rename filename column
sums <- sums %>% 
  separate_wider_delim(Filename, delim = "_", names = c(NA, NA, "Model", "Model2"), too_many = "drop", too_few = "align_start") %>%
  mutate(Model2 = if_else(str_detect(Model2, "\\."), Model2, NA_character_)) %>%
  separate(Model2, into = c("Model2", NA), sep = "\\.", extra = "drop", fill = "right") %>%
  unite("Model", Model:Model2, na.rm = TRUE)
```


# Class Count 

Let's merge and summarize class proportion estimates from different latent trajectory analysis (LTA) models across multiple class solutions (2 to 6 classes). The goal is to compare how class proportions change across models with different distributions (Poisson vs. Negative Binomial) and different trajectory assumptions (Linear vs. Quadratic).
For the final analysis, quadratic models are removed, since they cannot be used in LTA with only three datapoints - so this is only a demonstration.

```{r, error=FALSE}
# Poisson Linear
class_p_linear <-class_m2_p_l$modelEstimated %>% full_join(class_m3_p_l$modelEstimated,by="class",suffix=c("_m2_p","_m3_p")) %>%
  full_join(class_m4_p_l$modelEstimated,by="class") %>%
  full_join(class_m5_p_l$modelEstimated,by='class',suffix=c("_m4_p","_m5_p")) %>%
  full_join(class_m6_p_l$modelEstimated,by="class") %>%
  rename(proportion_m6_p=proportion) %>%
  select(class,starts_with('prop')) %>% round(2)

# Poisson Quadratic
class_p_quadratic <-class_m2_p_q$modelEstimated %>% full_join(class_m3_p_q$modelEstimated,by="class",suffix=c("_m2_p","_m3_p")) %>%
  full_join(class_m4_p_q$modelEstimated,by="class") %>%
  full_join(class_m5_p_q$modelEstimated,by='class',suffix=c("_m4_p","_m5_p")) %>%
  full_join(class_m6_p_q$modelEstimated,by="class") %>%
  rename(proportion_m6_p=proportion) %>%
  select(class,starts_with('prop')) %>% round(2)


# NB Linear
class_nb_linear <-class_m2_nb_l$modelEstimated %>% full_join(class_m3_nb_l$modelEstimated,by="class",suffix=c("_m2_nb","_m3_nb")) %>%
  full_join(class_m4_nb_l$modelEstimated,by="class") %>%
  full_join(class_m5_nb_l$modelEstimated,by='class',suffix=c("_m4_nb","_m5_nb")) %>%
  full_join(class_m6_nb_l$modelEstimated,by="class") %>%
  rename(proportion_m6_nb=proportion) %>%
  select(class,starts_with('prop')) %>% round(2)

# NB Quadratic
class_nb_quadratic <-class_m2_nb_q$modelEstimated %>% full_join(class_m3_nb_q$modelEstimated,by="class",suffix=c("_m2_nb","_m3_nb")) %>%
  full_join(class_m4_nb_q$modelEstimated,by="class") %>%
  full_join(class_m5_nb_q$modelEstimated,by='class',suffix=c("_m4_nb","_m5_nb")) %>%
  full_join(class_m6_nb_q$modelEstimated,by="class") %>%
  rename(proportion_m6_nb=proportion) %>%
  select(class,starts_with('prop')) %>% round(2)
```