---
title: "Mania_Modelling"
author: "by_Jasmin_Doenicke"
date: "Step7"
output:
  html_document:
    toc: yes
    theme: united
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---

# STARTER Code
```{r setup, error = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "E:")
```

```{r, error=FALSE, message = FALSE}
knitr::opts_chunk$set(error = TRUE)
```

```{r, error = FALSE, message = FALSE}
library(tidyverse)
library(naniar)
library(officer)
library(janitor)


#set workind directory
setwd("E:")

#set theme
theme_set(theme_bw())
```



# PHYSICAL HEALTH
## Sleep 
```{r, error=FALSE}
sleep <- read_csv("E:/release_5.1/core/physical-health/ph_p_sds.csv")
sleep = subset(sleep, select = c("src_subject_id", "eventname", "sds_p_ss_total", "sds_p_ss_dims",
"sds_p_ss_sbd", "sds_p_ss_da", "sds_p_ss_swtd", "sds_p_ss_does", "sds_p_ss_shy"))

# select only baseline
unique(sleep$eventname)
sleep = subset(sleep, sleep$eventname == "baseline_year_1_arm_1")
```

### PLOT Total Sleep Score
```{r, error=FALSE}
# plot
ggplot(sleep, aes(x = sds_p_ss_total))+
  geom_histogram(binwidth = 1)+
  ggtitle("Sleep disturbances / Recent life events involving sleep disruption")

# mean and range
mean(na.omit(sleep$sds_p_ss_total))
sd(na.omit(sleep$sds_p_ss_total))
table(sleep$sds_p_ss_total)
```

### PLOT SDSC - Disorders of Initiating and Maintaining Sleep (DIMS)
```{r, error=FALSE}
# plot
ggplot(sleep, aes(x = sds_p_ss_dims))+
  geom_histogram(binwidth = 1)+
  ggtitle("Sleep - Disorders of Initiating and Maintaining Sleep (DIMS)")

# mean and range
mean(na.omit(sleep$sds_p_ss_dims))
sd(na.omit(sleep$sds_p_ss_dims))
table(sleep$sds_p_ss_dims)
```

### PLOT SDSC -  Sleep Breathing disorders (SBD)
```{r, error=FALSE}
# plot
ggplot(sleep, aes(x = sds_p_ss_sbd))+
  geom_histogram(binwidth = 1)+
  ggtitle("Sleep -  Sleep Breathing disorders (SBD)")

# mean and range
mean(na.omit(sleep$sds_p_ss_sbd))
sd(na.omit(sleep$sds_p_ss_sbd))
table(sleep$sds_p_ss_sbd)
```

### PLOT SDSC - Disorder of Arousal (DA)
```{r, error=FALSE}
# plot
ggplot(sleep, aes(x = sds_p_ss_da))+
  geom_histogram(binwidth = 1)+
  ggtitle("Sleep - Disorder of Arousal (DA)")

# mean and range
mean(na.omit(sleep$sds_p_ss_da))
sd(na.omit(sleep$sds_p_ss_da))
table(sleep$sds_p_ss_da)
```

### PLOT SDSC - Sleep-Wake transition Disorders (SWTD) 
```{r, error=FALSE}
# plot
ggplot(sleep, aes(x = sds_p_ss_swtd))+
  geom_histogram(binwidth = 1)+
  ggtitle("Sleep - Sleep-Wake transition Disorders (SWTD)")

# mean and range
mean(na.omit(sleep$sds_p_ss_swtd))
sd(na.omit(sleep$sds_p_ss_swtd))
table(sleep$sds_p_ss_swtd)
```

### PLOT SDSC - Disorders of Excessive Somnolence
```{r, error=FALSE}
# plot
ggplot(sleep, aes(x = sds_p_ss_does))+
  geom_histogram(binwidth = 1)+
  ggtitle("Sleep - Disorders of Excessive Somnolence")

# mean and range
mean(na.omit(sleep$sds_p_ss_does))
sd(na.omit(sleep$sds_p_ss_does))
table(sleep$sds_p_ss_does)
```

### PLOT SDSC - Sleep Hyperhydrosis
```{r, error=FALSE}
# plot
ggplot(sleep, aes(x = sds_p_ss_shy))+
  geom_histogram(binwidth = 1)+
  ggtitle("Sleep - Sleep Hyperhydrosis")

# mean and range
mean(na.omit(sleep$sds_p_ss_shy))
sd(na.omit(sleep$sds_p_ss_shy))
table(sleep$sds_p_ss_shy)
```



## Irritable Bowel Syndrome
```{r, error=FALSE, message = FALSE}
ibs <- read_csv("E:/release_5.1/core/mental-health/mh_p_cbcl.csv")
ibs = subset(ibs, select = c("cbcl_q49_p", "cbcl_q56c_p", "cbcl_q56f_p", "cbcl_q56g_p", "src_subject_id", "eventname")) # select necessary variables only
ibs = subset(ibs, ibs$eventname == "baseline_year_1_arm_1") # select only baseline

# create sum score
ibs$four_sum = ibs$cbcl_q49_p + ibs$cbcl_q56c_p + ibs$cbcl_q56f_p + ibs$cbcl_q56g_p
ibs$three_sum = ibs$cbcl_q56c_p + ibs$cbcl_q56f_p + ibs$cbcl_q56g_p
```

### PLOT 4-item IBS symptoms

This is a version I did not use in the Master's thesis!
```{r, error=FALSE}
# plot
ggplot(ibs, aes(x = four_sum))+
  geom_histogram(binwidth = 1)

# mean and range
mean(na.omit(ibs$four_sum))
sd(na.omit(ibs$four_sum))
table(ibs$four_sum)
```

### PLOT 3-item IBS symptoms

I usedthese three items for the IBS-score in the analysis, since a previous paper has done the same.
```{r, error=FALSE}
# plot
ggplot(ibs, aes(x = three_sum))+
  geom_histogram(binwidth = 1)

# mean and range
mean(na.omit(ibs$three_sum))
sd(na.omit(ibs$three_sum))
table(ibs$three_sum)
```

## Asthma
```{r, error=FALSE, message = FALSE}
ast <- read_csv("E:/release_5.1/core/physical-health/ph_p_mhx.csv")
asthma = subset(ast, select = c("src_subject_id", "eventname", "medhx_2a"))
asthma = subset(asthma, asthma$eventname == "baseline_year_1_arm_1") # select only baseline (other timepoints are NA anyways)
```

### PLOT Asthma
```{r, error=FALSE}
# plot - baseline only
ggplot(asthma, aes(x = medhx_2a))+
  geom_histogram(binwidth = 1) +
  ggtitle("Asthma - Baseline Only")

# plot mean and range - baseline only
mean(na.omit(asthma$medhx_2a))
sd(na.omit(asthma$medhx_2a))
table(asthma$medhx_2a)
```

## Obesity
```{r, error=FALSE, message = FALSE}
bmi <- read_csv("E:/release_5.1/core/physical-health/ph_y_anthro.csv")

# Calculate mean height and weight across measurements (alternatively: use anthroheightcalc & anthroweightcalc from dataset)
bmi <- bmi %>% mutate(height_mean_in = rowMeans(select(bmi, c(anthro_1_height_in, anthro2heightin, anthro3heightin)), na.rm = TRUE))
bmi <- bmi %>% mutate(weight_mean_lb = rowMeans(select(bmi, c(anthroweight1lb, anthroweight2lb, anthroweight3lb)), na.rm = TRUE))
bmi <- bmi %>% mutate(height_cm = height_mean_in*2.54, weight_kg = weight_mean_lb*0.45359237, height_m = height_cm/100) #conversion to metric


bmi <- bmi %>% mutate(BMI = weight_kg/(height_m^2)) #bmi calculation (kg/m2)
bmi <- bmi %>% replace_with_na(replace = list(BMI = c('NaN'))) #replace NA
bmi$bmiz <- scale(bmi$BMI,center=TRUE, scale=TRUE) #create bmi-z-score
summary(bmi$bmiz) #final bmi z-score.

bmi = subset(bmi, bmi$eventname == "baseline_year_1_arm_1") # select only baseline
```

### PLOT BMI Full Dataset
```{r, error=FALSE}
# plotting full dataset (height/cm)
ggplot(bmi, aes(height_cm, weight_kg))+ 
  geom_jitter(height = 2, width = 2) +
  geom_smooth(method = lm)+
  ggtitle("Full Baseline Dataset with Outliers")

# mean and range
mean(na.omit(bmi$BMI))
min(na.omit(bmi$BMI))
max(na.omit(bmi$BMI))
```

The BMI ranges from 2 to 3017! There seems to be some issues with data quality. Let's clean it up.

### PLOT BMI: removing +/- 5 z-score
```{r, error=FALSE, message = FALSE}
bmi_5 = bmi

# removing outliers
bmi_5<-bmi_5 %>%mutate(bmiz       = if_else(bmiz       < 5,  bmiz,      NA)) # not z-score over 5
bmi_5<-bmi_5 %>%mutate(bmiz       = if_else(bmiz       >-5,  bmiz,      NA)) # no z-score under 5

# remove faulty data without bmiz (it doesnt calculate bmiz and the 4 cases must be removed by hand)
bmi_5<-bmi_5 %>%mutate(BMI        = if_else(BMI        <1000,BMI,       NA)) # remove BMI> 1000 
```

```{r, error=FALSE}
ggplot(bmi_5, aes(height_cm, weight_kg))+ 
  geom_jitter(height = 2, width = 2) +
  geom_smooth(method = lm)+
  ylim(4, 125)+ # weight
  xlim(80, 210)        # height
  ggtitle("Baseline Dataset with +/-5 z-score outliers removed")

# plotting BMI distribution
ggplot(bmi_5, aes(x = BMI))+
  geom_histogram(binwidth = 1)+
  ggtitle("Baseline Dataset with +/-5 z-score outliers removed - BMI score")

# plotting BMI z-score distribution
ggplot(bmi_5, aes(x = bmiz))+
  geom_histogram(binwidth = 0.05)+
  ggtitle("Baseline Dataset with +/-5 z-score outliers removed - z score")

# mean and range - BMI
mean(na.omit(bmi_5$BMI))
min(na.omit(bmi_5$BMI))
max(na.omit(bmi_5$BMI))

# mean and range - weight
mean(na.omit(bmi_5$weight_kg))
min(na.omit(bmi_5$weight_kg))
max(na.omit(bmi_5$weight_kg))
```

There is still some unclean data, but removing those outliers would require more targeted intervention strategies. Let's try some.

### PLOT BMI: removing +/- 5 z-score PLUS removing under BMI 12

I did not exclude this data in my Master's thesis, as the 'lower limit of human survival' BMI of 12 is highly debated, and no universally accepted lower BMI thresholds exist, especially for children. Therefore, I retained these values for analysis. However, if you'd like to explore the impact of removing them, here is the code:

```{r, error=FALSE, message = FALSE}
# removing more outliers
bmi_5_twelve <-bmi_5 %>%mutate(BMI       = if_else(BMI       >= 12,  BMI,      NA)) # no BMI under 12
```

```{r, error=FALSE}
ggplot(bmi_5_twelve, aes(height_cm, weight_kg))+ 
  geom_jitter(height = 2, width = 2) +
  geom_smooth(method = lm)+
  ylim(18, 125)+ # weight
  xlim(80, 178)+      # height
  ggtitle("Baseline Dataset with +/-5 z-score outliers and BMI < 12 removed")

# plotting BMI distribution
ggplot(bmi_5_twelve, aes(x = BMI))+
  geom_histogram(binwidth = 1)+     
  ggtitle("Baseline Dataset with +/-5 z-score outliers and BMI < 12 removed - BMI score")

# plotting BMI z-score distribution
ggplot(bmi_5_twelve, aes(x = bmiz))+
  geom_histogram(binwidth = 0.05)+      
  ggtitle("Baseline Dataset with +/-5 z-score outliers and BMI < 12 removed - z score")

# mean and range - BMI
mean(na.omit(bmi_5_twelve$BMI))
min(na.omit(bmi_5_twelve$BMI))
max(na.omit(bmi_5_twelve$BMI))

# mean and range - Weight
mean(na.omit(bmi_5_twelve$weight_kg))
min(na.omit(bmi_5_twelve$weight_kg))
max(na.omit(bmi_5_twelve$weight_kg))
```

### PLOT BMI: removing +/- 5 zscores and also all underweight children

This is removing even more children, again an "underweight" BMI changes by age and gender, so this was not used for the analysis and is simply demonstrating different data cleaning options:

```{r, error=FALSE, message = FALSE}
# removing more outliers
bmi_5_und <-bmi_5 %>%mutate(BMI       = if_else(BMI       >= 14,  BMI,      NA)) # no BMI under 14
```

```{r, error=FALSE}
ggplot(bmi_5_und, aes(height_cm, weight_kg))+ 
  geom_jitter(height = 2, width = 2) +
  geom_smooth(method = lm)+
  ylim(18, 125)+ # weight
  xlim(80, 178)+      # height
  ggtitle("Baseline Dataset with +/-5 z-score outliers and all underweight children removed")

# plotting BMI distribution
ggplot(bmi_5_und, aes(x = BMI))+
  geom_histogram(binwidth = 1)+     
  ggtitle("Baseline Dataset with +/-5 z-score outliers and all underweight children removed - BMI score")

# plotting BMI z-score distribution
ggplot(bmi_5_und, aes(x = bmiz))+
  geom_histogram(binwidth = 0.05)+      
  ggtitle("Baseline Dataset with +/-5 z-score outliers and all underweight children - z score")

# mean and range - BMI
mean(na.omit(bmi_5_und$BMI))
min(na.omit(bmi_5_und$BMI))
max(na.omit(bmi_5_und$BMI))

# mean and range - Weight
mean(na.omit(bmi_5_und$weight_kg))
min(na.omit(bmi_5_und$weight_kg))
max(na.omit(bmi_5_und$weight_kg))
```


## Birth/pregnancy complications

pregnancy_cx = total sum of pregnancy complications. 
pregnancy_binary =  (0/1) any pregnancy complications.

obestric_cx = total sum of obstetric complications. 
obestric_binary = (0/1) any birth complications.

premature_binary = binary, born prematurely.
premature_weeks = amount of weeks premature.

csection_binary = (0/1) C-section.
smallbirth = (0/1) less than 2,5kg at birth.


For this analysis, categorical variables were used because the reported events occurred 10 years after they happened, making precise recall and continuous data reliability questionable. Categorizing the variables helps mitigate recall bias and ensures a more robust comparison across groups.

```{r, error=FALSE, message = FALSE}
baby_data <-read_csv("E:/release_5.1/core/physical-health/ph_p_dhx.csv")

baby_data <- baby_data %>% filter(str_detect(eventname,'baseline')) %>%
  select(src_subject_id,eventname, devhx_10a3_p, devhx_10b3_p, devhx_10c3_p, devhx_10d3_p, devhx_10e3_p, devhx_10f3_p, devhx_10g3_p, devhx_10h3_p, devhx_10i3_p, devhx_10j3_p, devhx_10k3_p, devhx_10l3_p,devhx_10m3_p, devhx_13_3_p, devhx_14a3_p, devhx_14b3_p, devhx_14c3_p, devhx_14d3_p, devhx_14e3_p, devhx_14f3_p, devhx_14g3_p, devhx_14h3_p, birth_weight_lbs, devhx_12a_p, devhx_12_p, devhx_13_3_p)

baby_data<- baby_data %>% replace_with_na_all(condition = ~.x == 999) #remove NA (999)

# Create sum scores
baby_data <- baby_data %>% 
  mutate(pregnancy_cx=rowSums(across(c(devhx_10a3_p, devhx_10b3_p, devhx_10c3_p, devhx_10d3_p, devhx_10e3_p, devhx_10f3_p, devhx_10g3_p, devhx_10h3_p, devhx_10i3_p, devhx_10j3_p, devhx_10k3_p, devhx_10l3_p, devhx_10m3_p)),na.rm=T),
         obstetric_cx=rowSums(across(c(devhx_14a3_p, devhx_14b3_p, devhx_14c3_p, devhx_14d3_p, devhx_14e3_p, devhx_14f3_p, devhx_14g3_p, devhx_14h3_p)), na.rm=T),
         pregnancy_binary = if_else(pregnancy_cx>0,1,0),
         obstetric_binary = if_else(obstetric_cx>0,1,0),
         premature_binary = devhx_12a_p,
         premature_weeks = devhx_12_p,
         csection_binary = devhx_13_3_p,
         smallbirth=if_else (birth_weight_lbs < 5.51156, 1, 0)) # 5.51156 lbs = 2.5kg


#only select required variables, remove the rest
baby_data <-baby_data %>% select(src_subject_id, pregnancy_cx, obstetric_cx, pregnancy_binary, obstetric_binary, premature_binary, premature_weeks, csection_binary, smallbirth)
             
```

### PLOT Pregnancy Complications - Sum Score

Not used in analysis.

```{r, error=FALSE}
ggplot(baby_data, aes(x = pregnancy_cx))+
  geom_histogram(binwidth = 1)+
  ggtitle("Sum of pregnancy complications")

# mean and range
mean(na.omit(baby_data$pregnancy_cx))
sd(na.omit(baby_data$pregnancy_cx))
table(baby_data$pregnancy_cx)
```

### PLOT Pregnancy Complications - Binary

Categorical variables were used in the analysis to reduce recall bias from events reported 10 years later.

```{r, error=FALSE}
ggplot(baby_data, aes(x = pregnancy_binary))+
  geom_histogram(binwidth = 1)+
  ggtitle("Pregnancy complications - Binary")

# mean and range
mean(na.omit(baby_data$pregnancy_binary))
sd(na.omit(baby_data$pregnancy_binary))
table(baby_data$pregnancy_binary)
```

### PLOT Obstetric Complications - Sum Score

Not used in analysis.

```{r, error=FALSE}
ggplot(baby_data, aes(x = obstetric_cx))+
  geom_histogram(binwidth = 1)+
  ggtitle("Sum of obstetric complications")

# mean and range
mean(na.omit(baby_data$obstetric_cx))
sd(na.omit(baby_data$obstetric_cx))
table(baby_data$obstetric_cx)
```

### PLOT Obstetric Complications - Binary

Categorical variables were used in the analysis to reduce recall bias from events reported 10 years later.

```{r, error=FALSE}
ggplot(baby_data, aes(x = obstetric_binary))+
  geom_histogram(binwidth = 1)+
  ggtitle("Obstetric complications - Binary")

# mean and range
mean(na.omit(baby_data$obstetric_binary))
sd(na.omit(baby_data$obstetric_binary))
table(baby_data$obstetric_binary)
```

### PLOT Premature birth - in Weeks

Not used in analysis.

```{r}
ggplot(baby_data, aes(x = premature_weeks))+
  geom_histogram(binwidth = 1)+
  ggtitle("Amount of Weeks born prematurely")

# mean and range
mean(na.omit(baby_data$premature_weeks))
median(na.omit(baby_data$premature_weeks))
sd(na.omit(baby_data$premature_weeks))
table(baby_data$premature_weeks)
```

### PLOT Premature birth - Binary

Categorical variables were used in the analysis to reduce recall bias from events reported 10 years later.

```{r}
ggplot(baby_data, aes(x = premature_binary))+
  geom_histogram(binwidth = 1)+
  ggtitle("Premature birth - binary")

# mean and range
mean(na.omit(baby_data$premature_binary))
median(na.omit(baby_data$premature_binary))
sd(na.omit(baby_data$premature_binary))
table(baby_data$premature_binary)
```

### PLOT Small at birth - Binary
```{r}
ggplot(baby_data, aes(x = smallbirth))+
  geom_histogram(binwidth = 1)+
  ggtitle("Small at birth (under 2.5kg)")

#mean and range
mean(na.omit(baby_data$smallbirth))
sd(na.omit(baby_data$smallbirth))
table(baby_data$smallbirth)
```

### PLOT C-Section - Binary
```{r}
ggplot(baby_data, aes(x = csection_binary))+
  geom_histogram(binwidth = 1)+
  ggtitle("C-Section binary")

# mean and range
mean(na.omit(baby_data$csection_binary))
sd(na.omit(baby_data$csection_binary))
table(baby_data$csection_binary)
```

# MENTAL HEALTH
## Depression
```{r, error=FALSE, message = FALSE}
depression <- read_csv("E:/release_5.1/core/mental-health/mh_p_cbcl.csv")
depression = subset(depression, select = c("src_subject_id", "eventname", "cbcl_scr_dsm5_depress_t", "cbcl_scr_dsm5_depress_r"))
# Use only baseline
depression = subset(depression, depression$eventname == "baseline_year_1_arm_1")
```

### PLOT Depress CBCL DSM5 Scale t-score
```{r, error=FALSE}
ggplot(depression, aes(x = cbcl_scr_dsm5_depress_t))+
  geom_histogram(binwidth = 1)+
  ggtitle("CBCL depression DSM5 scale using t-score")

# mean and range
mean(na.omit(depression$cbcl_scr_dsm5_depress_t))
sd(na.omit(depression$cbcl_scr_dsm5_depress_t))
table(depression$cbcl_scr_dsm5_depress_t)
```

### PLOT Depress CBCL DSM5 Scale raw-score
```{r, error=FALSE}
ggplot(depression, aes(x = cbcl_scr_dsm5_depress_r))+
  geom_histogram(binwidth = 1)+
  ggtitle("CBCL depression DSM5 scale using raw-score")

# mean and range
mean(na.omit(depression$cbcl_scr_dsm5_depress_r))
sd(na.omit(depression$cbcl_scr_dsm5_depress_r))
table(depression$cbcl_scr_dsm5_depress_r)
```


## Anxiety
```{r}
anxiety <- read_csv("E:/release_5.1/core/mental-health/mh_p_cbcl.csv")
anxiety = subset(anxiety, select = c("src_subject_id", "eventname", "cbcl_scr_dsm5_anxdisord_t", "cbcl_scr_dsm5_anxdisord_r"))
anxiety = subset(anxiety, anxiety$eventname == "baseline_year_1_arm_1") # select only baseline
```

### PLOT AnxDisord CBCL DSM5 Scale t-score
```{r, error=FALSE}
# plot
ggplot(anxiety, aes(x = cbcl_scr_dsm5_anxdisord_t))+
  geom_histogram(binwidth = 1)+
  ggtitle("Anxiety using t-score")

# mean and range
mean(na.omit(anxiety$cbcl_scr_dsm5_anxdisord_t))
sd(na.omit(anxiety$cbcl_scr_dsm5_anxdisord_t))
table(anxiety$cbcl_scr_dsm5_anxdisord_t)
```

### PLOT AnxDisord CBCL DSM5 raw-score
```{r, error=FALSE}
# plot
ggplot(anxiety, aes(x = cbcl_scr_dsm5_anxdisord_r))+
  geom_histogram(binwidth = 1)+
  ggtitle("Anxiety using raw-score")

# mean and range
mean(na.omit(anxiety$cbcl_scr_dsm5_anxdisord_r))
sd(na.omit(anxiety$cbcl_scr_dsm5_anxdisord_r))
table(anxiety$cbcl_scr_dsm5_anxdisord_r)
```

## ADHD
```{r}
adhd <- read_csv("E:/release_5.1/core/mental-health/mh_p_cbcl.csv")
adhd = subset(adhd, select = c("src_subject_id", "eventname", "cbcl_scr_dsm5_adhd_t", "cbcl_scr_dsm5_adhd_r"))
# Use only baseline
adhd = subset(adhd, adhd$eventname == "baseline_year_1_arm_1")
```

### PLOT ADHD CBCL DSM5 Scale t-score
```{r, error=FALSE}
ggplot(adhd, aes(x = cbcl_scr_dsm5_adhd_t))+
  geom_histogram(binwidth = 1)+
  ggtitle("ADHD CBCL DSM5 Scale (t-score)")

# mean and range
mean(na.omit(adhd$cbcl_scr_dsm5_adhd_t))
sd(na.omit(adhd$cbcl_scr_dsm5_adhd_t))
table(adhd$cbcl_scr_dsm5_adhd_t)
```

### PLOT ADHD CBCL DSM5 Scale raw-score
```{r, error=FALSE}
ggplot(adhd, aes(x = cbcl_scr_dsm5_adhd_r))+
  geom_histogram(binwidth = 1)+
  ggtitle("ADHD CBCL DSM5 Scale (raw score)")

# mean and range
mean(na.omit(adhd$cbcl_scr_dsm5_adhd_r))
sd(na.omit(adhd$cbcl_scr_dsm5_adhd_r))
table(adhd$cbcl_scr_dsm5_adhd_r)
```


## Oppossitional Defiant Disorder
```{r, error=FALSE, message = FALSE}
opposition <- read_csv("E:/release_5.1/core/mental-health/mh_p_cbcl.csv")
opposition = subset(opposition, select = c("src_subject_id", "eventname", "cbcl_scr_dsm5_opposit_t", "cbcl_scr_dsm5_opposit_r"))
# Use only baseline
opposition = subset(opposition, opposition$eventname == "baseline_year_1_arm_1")
```

### PLOT CBCL opposition DSM5 scale t-score
```{r, error=FALSE}
ggplot(opposition, aes(x = cbcl_scr_dsm5_opposit_t))+
  geom_histogram(binwidth = 1)+
  ggtitle("ADHD CBCL DSM5 Scale (t-score)")

# mean and range
mean(na.omit(opposition$cbcl_scr_dsm5_opposit_t))
sd(na.omit(opposition$cbcl_scr_dsm5_opposit_t))
table(opposition$cbcl_scr_dsm5_opposit_t)
```

### PLOT CBCL opposition DSM5 scale raw score
```{r, error=FALSE}
ggplot(opposition, aes(x = cbcl_scr_dsm5_opposit_r))+
  geom_histogram(binwidth = 1)+
  ggtitle("ADHD CBCL DSM5 Scale (raw score)")

# mean and range
mean(na.omit(opposition$cbcl_scr_dsm5_opposit_r))
sd(na.omit(opposition$cbcl_scr_dsm5_opposit_r))
table(opposition$cbcl_scr_dsm5_opposit_r)
```

## Conduct Disorder
```{r, error=FALSE, message = FALSE}
conduct <- read_csv("E:/release_5.1/core/mental-health/mh_p_cbcl.csv")
conduct = subset(conduct, select = c("src_subject_id", "eventname", "cbcl_scr_dsm5_conduct_t", "cbcl_scr_dsm5_conduct_r"))
# Use only baseline
conduct = subset(conduct, conduct$eventname == "baseline_year_1_arm_1")
```

### PLOT CBCL conduct DSM5 scale t-score
```{r, error=FALSE}
ggplot(conduct, aes(x = cbcl_scr_dsm5_conduct_t))+
  geom_histogram(binwidth = 1)+
  ggtitle("ADHD CBCL DSM5 Scale (t-score)")

# mean and range
mean(na.omit(conduct$cbcl_scr_dsm5_conduct_t))
sd(na.omit(conduct$cbcl_scr_dsm5_conduct_t))
table(conduct$cbcl_scr_dsm5_conduct_t)
```

### PLOT CBCL conduct DSM5 scale raw score
```{r, error=FALSE}
ggplot(conduct, aes(x = cbcl_scr_dsm5_conduct_r))+
  geom_histogram(binwidth = 1)+
  ggtitle("ADHD CBCL DSM5 Scale (raw score)")

# mean and range
mean(na.omit(conduct$cbcl_scr_dsm5_conduct_r))
sd(na.omit(conduct$cbcl_scr_dsm5_conduct_r))
table(conduct$cbcl_scr_dsm5_conduct_r)
```


## Chronic stress/ stressful life events
```{r, error=FALSE, message = FALSE}
stress <- read_csv("E:/release_5.1/core/mental-health/mh_p_cbcl.csv")

stress = subset(stress, select = c("src_subject_id", "eventname", "cbcl_scr_07_stress_t", "cbcl_scr_07_stress_r"))
stress = subset(stress, stress$eventname == "baseline_year_1_arm_1") # select only baseline
```

### PLOT Stress t-score
```{r, error=FALSE}
# plot
ggplot(stress, aes(x = cbcl_scr_07_stress_t))+
  geom_histogram(binwidth = 3)

# mean and range
mean(na.omit(stress$cbcl_scr_07_stress_t))
sd(na.omit(stress$cbcl_scr_07_stress_t))
table(stress$cbcl_scr_07_stress_t)
```

### PLOT Stress raw score
```{r, error=FALSE}
# plot
ggplot(stress, aes(x = cbcl_scr_07_stress_r))+
  geom_histogram(binwidth = 3)

# mean and range
mean(na.omit(stress$cbcl_scr_07_stress_r))
sd(na.omit(stress$cbcl_scr_07_stress_r))
table(stress$cbcl_scr_07_stress_r)
```

# COGNITION

## Verbal memory - Rey Auditory Verbal Learning Test
```{r, error=FALSE, message = FALSE}
ravlt<-read_csv("E:/release_5.1/core/neurocognition/nc_y_ravlt.csv")

ravlt<-ravlt %>% filter(str_detect(eventname,'baseline')) %>% 
  select(src_subject_id,ends_with("tc"))

#score the RAVLT
ravlt<-ravlt %>% mutate(ravlt_learning=rowSums(across(c(pea_ravlt_sd_trial_i_tc:pea_ravlt_sd_trial_v_tc)),na.rm=T)) %>%
  rename(ravlt_distract=pea_ravlt_sd_listb_tc,
         ravlt_short=pea_ravlt_sd_trial_vi_tc,
         ravlt_long=pea_ravlt_ld_trial_vii_tc)
#remove other variables
ravlt<-ravlt %>% select(src_subject_id,starts_with("ravlt"))
```

### PLOT Verbal Memory "Learning"
```{r, error=FALSE}
ggplot(ravlt, aes(x = ravlt_learning))+
  geom_histogram(binwidth = 1)

# mean and range
mean(na.omit(ravlt$ravlt_learning))
sd(na.omit(ravlt$ravlt_learning))
table(ravlt$ravlt_learning)
```


# FAMILY
## Family conflict & criticism
```{r, error=FALSE, message = FALSE}
conflict_p <- read_csv("E:/release_5.1/core/culture-environment/ce_p_fes.csv")
conflict_p = subset(conflict_p, select = c("src_subject_id", "eventname", "fes_p_ss_fc")) # select relevant variable
conflict_p = subset(conflict_p, conflict_p$eventname == "baseline_year_1_arm_1") # select only baseline

conflict_y <- read_csv("E:/release_5.1/core/culture-environment/ce_y_fes.csv")
conflict_y = subset(conflict_y, select = c("src_subject_id", "eventname", "fes_y_ss_fc")) # select relevant variable
conflict_y = subset(conflict_y, conflict_y$eventname == "baseline_year_1_arm_1") # select only baseline
```

### PLOT Parent Report Sum Score - Family Conflict
```{r, error=FALSE}
ggplot(conflict_p, aes(x = fes_p_ss_fc))+
  geom_histogram(binwidth = 1)+
  ggtitle("Parent Report Sum Score - Family Conflict")

# mean and range
mean(na.omit(conflict_p$fes_p_ss_fc))
sd(na.omit(conflict_p$fes_p_ss_fc))
table(conflict_p$fes_p_ss_fc)
```

### PLOT Youth Report Sum Score - Family Conflict
```{r, error=FALSE, message = FALSE}
ggplot(conflict_y, aes(x = fes_y_ss_fc))+
  geom_histogram(binwidth = 1)+
  ggtitle("Youth Report Sum Score - Family Conflict")

# mean and range
mean(na.omit(conflict_y$fes_y_ss_fc))
sd(na.omit(conflict_y$fes_y_ss_fc))
table(conflict_y$fes_y_ss_fc)
```



## Childhood Trauma
```{r, error=FALSE, message = FALSE}
trauma<-read_csv("E:/release_5.1/core/mental-health/mh_p_ksads_ptsd.csv")
trauma<-trauma %>% filter(str_detect(eventname,'baseline')) %>% remove_empty() # select baseline

# create total variable
trauma<- trauma %>% mutate(total_PTSD=rowSums(across(c(ksads_ptsd_raw_754_p: ksads_ptsd_raw_770_p))))

#create maltreatment variable 
trauma<- trauma %>% mutate(maltreatment=rowSums(across(c(ksads_ptsd_raw_761_p:ksads_ptsd_raw_765_p,ksads_ptsd_raw_767_p:ksads_ptsd_raw_769_p))))
```

### PLOT Trauma
```{r, error=FALSE}
ggplot(trauma, aes(x = total_PTSD))+
  geom_histogram(binwidth = 1)+
  ggtitle("Trauma")

# mean and range
mean(na.omit(trauma$total_PTSD))
sd(na.omit(trauma$total_PTSD))
table(trauma$total_PTSD)
```


## Childhood Maltreatment

Here, I create a new 'maltreatment' variable by reversing emotional warmth scores to represent emotional neglect and incorporating maltreatment data from the KSADS.

```{r, error=FALSE, message = FALSE}
emotional_warmth<-read_csv("E:/release_5.1/core/culture-environment/ce_y_crpbi.csv")
emotional_warmth<-emotional_warmth %>% filter(str_detect(eventname,'baseline')) %>% remove_empty() # select baseline

# create total variable
emotional_warmth<- emotional_warmth %>% mutate(emo_neglect=rowSums(across(c(crpbi_parent1_y: crpbi_parent5_y))))

# create binary variable (0 = no neglect, 1 = neglect)
# 1 = "not like him" = emotional neglect. 2 or 3 = "somewhat/ a lot like him" = no neglect.
emotional_warmth$crpbi_parent1_y_binary <- ifelse(emotional_warmth$crpbi_parent1_y == 1, 1, 0)
emotional_warmth$crpbi_parent2_y_binary <- ifelse(emotional_warmth$crpbi_parent2_y == 1, 1, 0)
emotional_warmth$crpbi_parent3_y_binary <- ifelse(emotional_warmth$crpbi_parent3_y == 1, 1, 0)
emotional_warmth$crpbi_parent4_y_binary <- ifelse(emotional_warmth$crpbi_parent4_y == 1, 1, 0)
emotional_warmth$crpbi_parent5_y_binary <- ifelse(emotional_warmth$crpbi_parent5_y == 1, 1, 0)

emotional_warmth<- emotional_warmth %>% mutate(emotional_warmth_binary =rowSums(across(c(crpbi_parent1_y_binary: crpbi_parent5_y_binary))))


# select the two necessary datasets
maltreatment_neglect_data = subset(trauma, select = c("src_subject_id", "maltreatment")) # select
maltreatment_neglect_data2 = subset(emotional_warmth, select = c("src_subject_id", "emotional_warmth_binary")) # select

# join the two datasets by subject ID
maltreatment_neglect = full_join(maltreatment_neglect_data, maltreatment_neglect_data2, by = "src_subject_id")

# clean leftover datasets
rm(maltreatment_neglect_data)
rm(maltreatment_neglect_data2)

# check correlation
#cor(na.omit(maltreatment_neglect$maltreatment, maltreatment_neglect$emotional_warmth_binary))

# add into 1 variable
maltreatment_neglect<- maltreatment_neglect %>% mutate(mal_neglect=rowSums(across(c(maltreatment, emotional_warmth_binary))))
```

### PLOT Maltreatment
```{r, error=FALSE }
ggplot(maltreatment_neglect, aes(x = mal_neglect))+
  geom_histogram(binwidth = 1)+
  ggtitle("Maltreatment")

# mean and range
mean(na.omit(maltreatment_neglect$mal_neglect))
sd(na.omit(maltreatment_neglect$mal_neglect))
table(maltreatment_neglect$mal_neglect)
```



## Family history of mania - First-Degree Relatives

They were measured only at baseline! data = fam_first. variable = family_mania

```{r, error=FALSE, message = FALSE}
fam_first<-read_csv("E:/release_5.1/core/mental-health/mh_p_fhx.csv")
unique(fam_first$eventname) # => this shows us all data is already only at baseline
fam_first <- fam_first %>% select(src_subject_id, famhx_ss_fath_prob_ma_p,famhx_ss_moth_prob_ma_p, famhx_ss_fulsiby1_prob_ma_p, famhx_ss_fulsiby2_prob_ma_p, famhx_ss_fulsiby3_prob_ma_p, famhx_ss_fulsiby4_prob_ma_p, famhx_ss_fulsiby5_prob_ma_p, famhx_ss_fulsibo1_prob_ma_p, famhx_ss_fulsibo2_prob_ma_p, famhx_ss_fulsibo3_prob_ma_p, famhx_ss_fulsibo4_prob_ma_p, famhx_ss_fulsibo5_prob_ma_p) # select variables

fam_first<-fam_first %>% mutate(sum_history=rowSums(across(c(famhx_ss_fath_prob_ma_p, famhx_ss_moth_prob_ma_p, famhx_ss_fulsiby1_prob_ma_p, famhx_ss_fulsiby2_prob_ma_p, famhx_ss_fulsiby3_prob_ma_p, famhx_ss_fulsiby4_prob_ma_p, famhx_ss_fulsiby5_prob_ma_p, famhx_ss_fulsibo1_prob_ma_p, famhx_ss_fulsibo2_prob_ma_p, famhx_ss_fulsibo3_prob_ma_p, famhx_ss_fulsibo4_prob_ma_p, famhx_ss_fulsibo5_prob_ma_p)),na.rm=T)) # sum score 

fam_first<-fam_first %>% mutate(family_mania=if_else(sum_history>0,1,0))  # binary score (yes/no)
```

### PLOT First-Degree Relatives, Binary 

This is the relatives variables that was used in analysis. Still, let's have a look at other options, too! 

```{r, error=FALSE}
table(fam_first$family_mania)#check N of people with family history

ggplot(fam_first, aes(x = family_mania))+
  geom_histogram(binwidth = 1)+
  ggtitle("Family history of mania - First Degree - Binary")
```

### PLOT First-Degree Relatives, Sum Score 
```{r, error=FALSE}
table(fam_first$sum_history) # sum score
mean(fam_first$sum_history)
sd(fam_first$sum_history)

ggplot(fam_first, aes(x = sum_history))+
  geom_histogram(binwidth = 1)+
  ggtitle("Family history of mania - First Degree - Sum Score")
```



## Family history of mania - First and Second Degree Relatives

This was not used in analysis, since previous works focused on first-degree relatives.

```{r, error=FALSE, message = FALSE}
famhx<-read_csv("E:/release_5.1/core/mental-health/mh_p_fhx.csv")
unique(famhx$eventname) # => this shows us all data is already only at baseline
famhx <- famhx %>% select(src_subject_id,famhx_ss_fath_prob_ma_p:famhx_ss_fulsibo5_prob_ma_p) # select variables
famhx<-famhx %>% mutate(sum_hx=rowSums(across(2:37),na.rm=T)) # sum score 
famhx<-famhx %>% mutate(famhx_mania=if_else(sum_hx>0,1,0)) # binary score (yes/no)
```

### PLOT First and Second Degree Relatives, Binary 
```{r, error=FALSE}
table(famhx$famhx_mania) #check N of people with family history

ggplot(famhx, aes(x = famhx_mania))+
  geom_histogram(binwidth = 1)+
  ggtitle("Family history of mania - First and Second Degree - Binary")
```


### PLOT First and Second Degree Relatives, Sum Score
```{r}
table(famhx$sum_hx) #check sum score
mean(na.omit(famhx$sum_hx))
sd(na.omit(famhx$sum_hx))

ggplot(famhx, aes(x = sum_hx))+
  geom_histogram(binwidth = 1)+
  ggtitle("Family history of mania - First and Second Degree - Sum Score")
```






# Check Demographics
```{r, error=FALSE, message = FALSE}
load(file='E:/data/GBI_demographics.rdata') 
GBI_demographics = subset(GBI_demographics, GBI_demographics$eventname == "baseline_year_1_arm_1")
```

### Sex
```{r, error=FALSE}
table(GBI_demographics$demo_sex_v2)
mean(na.omit(GBI_demographics$demo_sex_v2))
```

### Ethnicity and Race
```{r, error=FALSE}
# race
table(GBI_demographics$race)

# hispanic ethnicity
table(GBI_demographics$ethnicity)
```



# RISK FACTOR DATASET
## Finalize Riskfactor Dataset
```{r}
riskfactors <-sleep %>% select(src_subject_id,eventname,sds_p_ss_total) %>% 
  full_join(ibs) %>%                                                            
  full_join(asthma) %>%                                                          
  full_join(bmi_5_twelve) %>%  # bmi without outliers z > +/-5 or under life limit
  full_join(baby_data) %>%
  full_join(depression) %>%
  full_join(anxiety) %>%
  full_join(adhd) %>%
  full_join(opposition) %>%
  full_join(conduct) %>%
  full_join(stress) %>%
  full_join(ravlt) %>%
  full_join(conflict_p) %>%
  full_join(conflict_y) %>%
  full_join(trauma) %>%
  full_join(maltreatment_neglect) %>%
  full_join(fam_first) 

## keep only relevant variables
riskfactors = subset(new_riskfactors, select = c("src_subject_id", "eventname", "sds_p_ss_total", "three_sum", "medhx_2a", "BMI", "pregnancy_binary", "obstetric_binary", "premature_binary", "smallbirth", "csection_binary", "cbcl_scr_dsm5_depress_r", "cbcl_scr_dsm5_anxdisord_r", "cbcl_scr_dsm5_adhd_r", "cbcl_scr_dsm5_opposit_r", "cbcl_scr_dsm5_conduct_r", "cbcl_scr_07_stress_r", "ravlt_learning", "fes_p_ss_fc", "fes_y_ss_fc", "total_PTSD", "mal_neglect", "family_mania"))

# keep only baseline
new_riskfactors = subset(new_riskfactors, new_riskfactors$eventname == "baseline_year_1_arm_1") 

# save dataset
#save(new_riskfactors,file='data/new_riskfactors.rdata') 
```



## Riskfactors: List of relevant variables
sds_p_ss_total                = sleep  
three_sum                     = IBS  
medhx_2a                      = asthma  
BMI                           = bmi  
pregnancy_binary              = any pregnancy complications  
obstetric_binary             = any obstetric complications  
premature_binary              = born early  
smallbirth                    = weight under 2.5kg at birth  
csection_binary               = C-Section  
cbcl_scr_dsm5_depress_r       = depression  
cbcl_scr_dsm5_anxdisord_r     = anxiety  
cbcl_scr_dsm5_adhd_r          = ADHD  
cbcl_scr_dsm5_opposit_r       = Oppositional behavior   
cbcl_scr_dsm5_conduct_r       = Conduct disorder behavior  
cbcl_scr_07_stress_r          = Stress  
ravlt_learning                = Ray Auditory Learning Test  
fes_p_ss_fc                   = Family Conflict - parent rating  
fes_y_ss_fc                   = Family Conflict - youth rating  
total_PTSD                    = Trauma  
mal_neglect                   = Maltreatment  
family_mania                  = any First_Degree Relatives  



## Create 1 final dataset
```{r}
rm(list = ls()) # clean all previous datasets
load(file='E:/data/new_riskfactors.rdata')  # load all riskfactors
load(file='E:/data/20240912_ses.rdata')     # load socioeconomic status
load(file='E:/data/GBI_demographics.rdata') # load GBI and demographics

# join datasets
new_GBI_demographics_riskfactors = left_join(GBI_demographics, ses)
new_GBI_demographics_riskfactors = left_join(new_GBI_demographics_riskfactors, new_riskfactors)

# save dataset
#save(new_GBI_demographics_riskfactors, file = 'data/new_GBI_demographics_riskfactors.rdata')
```


## Prepare for MPlus
```{r}
rm(list = ls()) # clean all previous datasets
load(file = 'E:/data/new_GBI_demographics_riskfactors.rdata') 
new_GBI_demographics_riskfactors %>% distinct(src_subject_id) %>% count() # this file has 11,868 participants

new_GBI_demographics_riskfactors <-new_GBI_demographics_riskfactors  %>% filter(!c(visit==3 |visit==4)) 
new_GBI_demographics_riskfactors %>% distinct(src_subject_id) %>% count() # still 11868 participants

new_GBI_demographics_riskfactors <- new_GBI_demographics_riskfactors %>% filter(!is.na(pgbi_p_ss_score)) 
new_GBI_demographics_riskfactors %>% distinct(src_subject_id) %>% count() # 11866 participants
 

new_GBI_demographics_riskfactors<-new_GBI_demographics_riskfactors %>% group_by(src_subject_id) %>% 
  mutate(count=n()) %>% 
  filter(count==3) %>% ungroup() %>%
  select(!c(eventname,count))
new_GBI_demographics_riskfactors %>% distinct(src_subject_id) %>% count() #10,634 participants (same as for the first MPLUS analysis)

# transform to wide format
data_wide<- new_GBI_demographics_riskfactors%>% pivot_wider(
  id_cols=c(src_subject_id, race,ethnicity,demo_sex_v2, income_to_needs), # these don't change over time
  names_from = visit,
  values_from = c(site,acs_raked_propensity_score,pgbi_p_ss_score, 
                 sds_p_ss_total,                # sleep
                 three_sum,                     # IBS
                 medhx_2a,                      # asthma
                 BMI,                           # bmi
                 pregnancy_binary,              # any pregnancy complications
                 obstetric_binary,              # any obstetric complications
                 premature_binary,              # born early
                 smallbirth,                    # weight under 2.5kg at birth
                 csection_binary,               # C-Section
                 cbcl_scr_dsm5_depress_r,       # depression
                 cbcl_scr_dsm5_anxdisord_r,     # anxiety
                 cbcl_scr_dsm5_adhd_r,          # ADHD
                 cbcl_scr_dsm5_opposit_r,       # Oppositional behavior
                 cbcl_scr_dsm5_conduct_r,       # Conduct disorder behavior
                 cbcl_scr_07_stress_r,          # Stress
                 ravlt_learning,                # Ray Auditory Learning Test
                 fes_p_ss_fc,                   # Family Conflict - parent rating
                 fes_y_ss_fc,                   # Family Conflict - youth rating
                 total_PTSD,                    # Trauma
                 mal_neglect,                   # Maltreatment and Neglect (score of 2 questionnaires)
                 family_mania))                 # any First_Degree Relatives))                        

# add race dummy variable
library(fastDummies)
data_wide<-data_wide %>% 
  dummy_cols(select_columns="race",remove_selected_columns = T,remove_first_dummy = T)


#Convert sex and ethnicity to numeric
data_wide<-data_wide %>% mutate(ethnicity=as.numeric(ethnicity),
                                demo_sex_v2=as.numeric(demo_sex_v2),
                                site_0=as.numeric(site_0))

#rearrange variables
data_wide<-data_wide %>% select(src_subject_id,site_0,acs_raked_propensity_score_0,
                                pgbi_p_ss_score_0, pgbi_p_ss_score_1, pgbi_p_ss_score_2 ,demo_sex_v2,
                                starts_with("race"),ethnicity, income_to_needs,
                                ends_with("_0"))


#replace missing with -99 (required for Mplus to work)
new_data_final<-data_wide %>% replace(is.na(.),-99)

##save data (id's included)
#setwd("E:")
#write.csv(new_data_final, file='code/MPLUS/new_data_predictors.csv',row.names = F)

##save data (id's and headers removed) ==> manually go into excel and remove headers
new_data_final <- new_data_final %>% select(-src_subject_id)
colnames(new_data_final)
#write.csv(new_data_final, file='code/MPLUS/new_data_predictors_noheaders.csv',row.names = F,col.names = F)
```



# SLEEP DATASET

for post-hoc analysis only; not part of the main hypotheses
```{r}
sleep <- read_csv("E:/release_5.1/core/physical-health/ph_p_sds.csv")
sleep = subset(sleep, select = c("src_subject_id", "eventname", "sds_p_ss_total", "sds_p_ss_dims",
"sds_p_ss_sbd", "sds_p_ss_da", "sds_p_ss_swtd", "sds_p_ss_does", "sds_p_ss_shy"))

sleep = subset(sleep, sleep$eventname == "baseline_year_1_arm_1") # select only baseline

sleep_dataset = subset(sleep, select = c ("src_subject_id", "eventname", "sds_p_ss_dims", "sds_p_ss_sbd", "sds_p_ss_da", "sds_p_ss_swtd", "sds_p_ss_does", "sds_p_ss_shy"))
 
# save dataset
# save(sleep_dataset,file='data/sleep_dataset.rdata') 

# Create one final dataset
load(file='E:/data/20240912_ses.rdata')     # load socioeconomic status
load(file='E:/data/GBI_demographics.rdata') # load GBI and demographics

# join datasets
sleep_with_GBIdemographics = left_join(GBI_demographics, ses)
sleep_with_GBIdemographics = left_join(sleep_with_GBIdemographics, sleep_dataset)

# save dataset
# save(sleep_with_GBIdemographics, file = 'data/sleep_with_GBIdemographics.rdata')
```

## Prepare Sleep Dataset for MPlus
```{r}
rm(list = ls()) # clean all previous datasets
load(file = 'E:/data/sleep_with_GBIdemographics.rdata') 
sleep_with_GBIdemographics %>% distinct(src_subject_id) %>% count() # this file has 11,868 participants

sleep_with_GBIdemographics <-sleep_with_GBIdemographics  %>% filter(!c(visit==3 |visit==4)) 
sleep_with_GBIdemographics %>% distinct(src_subject_id) %>% count() # still 11868 participants

sleep_with_GBIdemographics <- sleep_with_GBIdemographics %>% filter(!is.na(pgbi_p_ss_score)) 
sleep_with_GBIdemographics %>% distinct(src_subject_id) %>% count() # 11866 participants
 

sleep_with_GBIdemographics<-sleep_with_GBIdemographics %>% group_by(src_subject_id) %>% 
  mutate(count=n()) %>% 
  filter(count==3) %>% ungroup() %>%
  select(!c(eventname,count))
sleep_with_GBIdemographics %>% distinct(src_subject_id) %>% count() #10,634 participants (same as for the first MPLUS analysis)

# transform to wide format
data_wide<- sleep_with_GBIdemographics%>% pivot_wider(
  id_cols=c(src_subject_id, race,ethnicity,demo_sex_v2, income_to_needs), # these don't change over time
  names_from = visit,
  values_from = c(site,acs_raked_propensity_score,pgbi_p_ss_score, 
                 sds_p_ss_dims, # Sleep Subscale - Disorders of Initiating and Maintaining Sleep
                 sds_p_ss_sbd,  # Sleep Subscale - Sleep Breathing disorders
                 sds_p_ss_da,   # Sleep Subscale - Disorder of Arousal 
                 sds_p_ss_swtd, # Sleep Subscale - Sleep-Wake transition Disorders
                 sds_p_ss_does, # Sleep Subscale - Disorders of Excessive Somnolence
                 sds_p_ss_shy)) # Sleep Subscale - Sleep Hyperhydrosis                                    

# add race dummy variable
library(fastDummies)
data_wide<-data_wide %>% 
  dummy_cols(select_columns="race",remove_selected_columns = T,remove_first_dummy = T)


#Convert sex and ethnicity to numeric
data_wide<-data_wide %>% mutate(ethnicity=as.numeric(ethnicity),
                                demo_sex_v2=as.numeric(demo_sex_v2),
                                site_0=as.numeric(site_0))

#rearrange variables
data_wide<-data_wide %>% select(src_subject_id,site_0,acs_raked_propensity_score_0,
                                pgbi_p_ss_score_0, pgbi_p_ss_score_1, pgbi_p_ss_score_2 ,demo_sex_v2,
                                starts_with("race"),ethnicity, income_to_needs,
                                ends_with("_0"))


#replace missing with -99 (required for Mplus to work)
new_data_final<-data_wide %>% replace(is.na(.),-99)
```

## Save Sleep Dataset

Save the dataset with IDs for clarity and without IDs and headers for Mplus analysis. 

```{r}
sleep_dataset = new_data_final 

##save data (id's included)
#write.csv(sleep_dataset, file='code/MPLUS/sleep_dataset.csv',row.names = F)

##save data (id's and headers removed)
sleep_dataset <- sleep_dataset %>% select(-src_subject_id)
colnames(sleep_dataset)
#write.csv(sleep_dataset, file='code/MPLUS/sleep_dataset_noheaders.csv',row.names = F,col.names = F)
```





