
---
title: "Mania_Modelling"
author: "by_Jasmin_Doenicke"
date: "Step 9"
output:
  html_document:
    toc: yes
    theme: united
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---
# STARTER Code
```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "E:/Masterarbeit")
getwd()

# turn off all warning messages
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(error = TRUE)
```

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(janitor)
library(effectsize)
library(MplusAutomation)


#set working directory
setwd("E:/Masterarbeit")

#set theme
theme_set(theme_bw())
```

# Read In Risk Factors


## Sleep
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/01_sleep.out', header=F,skip=531,sep=" ")

sleep<-data[c(2,14,26),c(5, 19,25,30,36)]
sleep<-sleep %>% mutate(across(2:5,as.numeric))
sleep<-sleep %>% remove_empty()
colnames(sleep)<-c("var",'est','se','t','p')


sleep<-sleep %>% mutate(class=c("1","2",'3'))

sleep
```

## IBS
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/02_ibs.out', header = FALSE ,skip=531,sep=" ")
ibs<-data[c(2,13,24),c(5:39)]
ibs <- data[c(2,13,24), c(5, 21, 27, 32, 33, 38, 39)]
ibs <- ibs %>%
  mutate(across(2:7, as.numeric))


# Combine columns by removing NAs
ibs$C45 <- ifelse(!is.na(ibs$V32), ibs$V32, ibs$V33)
ibs$C67 <- ifelse(!is.na(ibs$V38), ibs$V38, ibs$V39)

# Reorder columns to place the new column in the original position of Column 1 and 2
#ibs <- ibs[, c("Column1and2", setdiff(names(data), c("Column1", "Column2")))]

# Remove the original columns
ibs <- ibs[, !names(ibs) %in% c("V32", "V33", "V38", "V39")]



colnames(ibs)<-c("var",'est','se','t','p')
ibs<-ibs %>% mutate(class=c("1","2",'3'))

ibs
```

## Asthma
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/03_asthma.out', header = FALSE ,skip=531,sep=" ")

asthma<-data[c(2,14,26),c(5:37)]
asthma<-data[c(2,14,26),c(5,18, 24,30, 36)]
asthma<-asthma %>% mutate(across(2:5,as.numeric))
colnames(asthma)<-c("var",'est','se','t','p')


asthma<-asthma %>% mutate(class=c("1","2",'3'))

asthma
```

## BMI
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/04_bmi.out', header = FALSE ,skip=531,sep=" ")

bmi<-data[c(2,13,24),c(5:ncol(data))]
bmi<-data[c(2,13,24),c(5, 21, 27, 33, 39)]
bmi<-bmi %>% mutate(across(2:5,as.numeric))
colnames(bmi)<-c("var",'est','se','t','p')


bmi<-bmi %>% mutate(class=c("1","2",'3'))

bmi
```

## Preg
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/05_preg.out', header = FALSE ,skip=531,sep=" ")

preg<-data[c(2,13,24),c(5:ncol(data))]
preg<-data[c(2,13,24),c(5, 20, 26, 32, 38)]
preg<-preg %>% mutate(across(2:5,as.numeric))
colnames(preg)<-c("var",'est','se','t','p')


preg<-preg %>% mutate(class=c("1","2",'3'))

preg
```

## Obst
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/06_obst.out', header = FALSE ,skip=531,sep=" ")

obst<-data[c(2,13,24),c(5:ncol(data))]
obst<-data[c(2,13,24),c(5, 20, 26, 32, 38)]
obst<-obst %>% mutate(across(2:5,as.numeric))
colnames(obst)<-c("var",'est','se','t','p')


obst<-obst %>% mutate(class=c("1","2",'3'))

obst
```

## Premat
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/07_premat.out', header = FALSE ,skip=531,sep=" ")

premat<-data[c(2,14,26),c(5:ncol(data))]
premat<-data[c(2,14,26),c(5, 17, 23, 28, 34)]
premat<-premat %>% mutate(across(2:5,as.numeric))
colnames(premat)<-c("var",'est','se','t','p')


premat<-premat %>% mutate(class=c("1","2",'3'))

premat
```

## Small
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/08_small.out', header = FALSE ,skip=531,sep=" ")

small<-data[c(2,14,26),c(5:ncol(data))]
small<-data[c(2,14,26),c(5, 18, 24, 29, 35)]
small<-small %>% mutate(across(2:5,as.numeric))
colnames(small)<-c("var",'est','se','t','p')


small<-small %>% mutate(class=c("1","2",'3'))

small
```

## C-Sect
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/09_csect.out', header = FALSE ,skip=531,sep=" ")

csect<-data[c(2,14,26),c(5:ncol(data))]
csect<-data[c(2,14,26),c(5, 18, 19, 24, 25, 29, 31, 35, 37)]
csect<-csect %>% mutate(across(2:9,as.numeric))


# Combine columns by removing NAs
csect$C18_19 <- ifelse(!is.na(csect$V18), csect$V18, csect$V19)
csect$C24_25 <- ifelse(!is.na(csect$V24), csect$V24, csect$V25)
csect$C29_31 <- ifelse(!is.na(csect$V29), csect$V29, csect$V31)
csect$C35_37 <- ifelse(!is.na(csect$V35), csect$V35, csect$V37)

# Remove the original columns
csect <- csect[, !names(csect) %in% c("V18", "V19", "V24", "V25", "V29", "V31", "V35", "V37")]


colnames(csect)<-c("var",'est','se','t','p')
csect<-csect %>% mutate(class=c("1","2",'3'))

csect
```


## Depress
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/10_depress.out', header = FALSE ,skip=534,sep=" ")

depress<-data[c(2,14,27),c(5:ncol(data))]
depress<-data[c(2,14,27),c(5, 17, 23, 28, 34)]
depress<-depress %>% mutate(across(2:5,as.numeric))
colnames(depress)<-c("var",'est','se','t','p')


depress<-depress %>% mutate(class=c("1","2",'3'))

depress
```

## Anx
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/11_anx.out', header = FALSE ,skip=531,sep=" ")

anx<-data[c(2,13,24),c(5:ncol(data))]
anx<-data[c(2,13,24),c(5, 21, 27, 32, 38)]
anx<-anx %>% mutate(across(2:5,as.numeric))
colnames(anx)<-c("var",'est','se','t','p')


anx<-anx %>% mutate(class=c("1","2",'3'))

anx
```

## ADHD
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/12_adhd.out', header = FALSE ,skip=531,sep=" ")

adhd<-data[c(2,13,24),c(5:ncol(data))]
adhd<-data[c(2,13,24),c(5, 20, 26, 31, 37)]
adhd<-adhd %>% mutate(across(2:5,as.numeric))
colnames(adhd)<-c("var",'est','se','t','p')


adhd<-adhd %>% mutate(class=c("1","2",'3'))

adhd
```

## Opposit
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/13_opposit.out', header = FALSE ,skip=534,sep=" ")

opposit<-data[c(2,13,24),c(5:ncol(data))]
opposit<-data[c(2,13,24),c(5, 17, 23, 28, 34)]
opposit<-opposit %>% mutate(across(2:5,as.numeric))
colnames(opposit)<-c("var",'est','se','t','p')


opposit<-opposit %>% mutate(class=c("1","2",'3'))

opposit
```


## Conduct
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/14_conduct.out', header = FALSE ,skip=534,sep=" ")

conduct<-data[c(2,13,24),c(5:ncol(data))]
conduct<-data[c(2,13,24),c(5, 17, 23, 28, 34)]
conduct<-conduct %>% mutate(across(2:5,as.numeric))
colnames(conduct)<-c("var",'est','se','t','p')


conduct<-conduct %>% mutate(class=c("1","2",'3'))

conduct
```

## Stress
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/15_stress.out', header = FALSE ,skip=531,sep=" ")

stress<-data[c(2,13,24),c(5:ncol(data))]
stress<-data[c(2,13,24),c(5, 18, 24, 29, 35)]
stress<-stress %>% mutate(across(2:5,as.numeric))
colnames(stress)<-c("var",'est','se','t','p')


stress<-stress %>% mutate(class=c("1","2",'3'))

stress
```

## Verbal Learning
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/16_ravlt.out', header = FALSE ,skip=531,sep=" ")

ravlt<-data[c(2,14,26),c(5:ncol(data))]
ravlt<-data[c(2,14,26),c(5, 18, 19, 24, 25, 29, 31, 35, 37)]
ravlt<-ravlt %>% mutate(across(2:9,as.numeric))


# Combine columns by removing NAs
ravlt$C18_19 <- ifelse(!is.na(ravlt$V18), ravlt$V18, ravlt$V19)
ravlt$C24_25 <- ifelse(!is.na(ravlt$V24), ravlt$V24, ravlt$V25)
ravlt$C29_31 <- ifelse(!is.na(ravlt$V29), ravlt$V29, ravlt$V31)
ravlt$C35_37 <- ifelse(!is.na(ravlt$V35), ravlt$V35, ravlt$V37)
# Remove the original columns
ravlt <- ravlt[, !names(ravlt) %in% c("V18", "V19", "V24", "V25", "V29", "V31", "V35", "V37")]


colnames(ravlt)<-c("var",'est','se','t','p')
ravlt<-ravlt %>% mutate(class=c("1","2",'3'))

ravlt
```

## Family Conflict - Parents
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/17_fes_p.out', header = FALSE ,skip=531,sep=" ")

fes_p<-data[c(2,14,26),c(5:ncol(data))]
fes_p<-data[c(2,14,26),c(5, 19, 25, 30, 36)]
fes_p<-fes_p %>% mutate(across(2:5,as.numeric))
colnames(fes_p)<-c("var",'est','se','t','p')


fes_p<-fes_p %>% mutate(class=c("1","2",'3'))

fes_p
```

## Family Conflict - Youth
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/18_fes_y.out', header = FALSE ,skip=531,sep=" ")

fes_y<-data[c(2,14,26),c(5:ncol(data))]
fes_y<-data[c(2,14,26),c(5, 19, 25, 31, 37)]
fes_y<-fes_y %>% mutate(across(2:5,as.numeric))
colnames(fes_y)<-c("var",'est','se','t','p')


fes_y<-fes_y %>% mutate(class=c("1","2",'3'))

fes_y
```

## Trauma
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/19_trauma.out', header = FALSE ,skip=531,sep=" ")

trauma<-data[c(2,14,26),c(5:ncol(data))]
trauma<-data[c(2,14,26),c(5, 18, 24, 30, 36)]
trauma<-trauma %>% mutate(across(2:5,as.numeric))
colnames(trauma)<-c("var",'est','se','t','p')


trauma<-trauma %>% mutate(class=c("1","2",'3'))

trauma
```

## Maltreatment
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/20_maltr.out', header = FALSE ,skip=531,sep=" ")

maltr<-data[c(2,14,26),c(5:ncol(data))]
maltr<-data[c(2,14,26),c(5, 19, 25, 31, 37)]
maltr<-maltr %>% mutate(across(2:5,as.numeric))
colnames(maltr)<-c("var",'est','se','t','p')


maltr<-maltr %>% mutate(class=c("1","2",'3'))

maltr
```

## First Degree Relatives
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/with_covariates/21_first_d.out', header = FALSE ,skip=534,sep=" ")

first_d<-data[c(2,14,26),c(5:ncol(data))]
first_d<-data[c(2,14,26),c(5, 17, 23, 29, 35)]
first_d<-first_d %>% mutate(across(2:5,as.numeric))
colnames(first_d)<-c("var",'est','se','t','p')


first_d<-first_d %>% mutate(class=c("1","2",'3'))

first_d
```


## Merge

```{r}
#now bind them together
pvals<-rbind(sleep, ibs, asthma, bmi,
preg, obst, premat, small, csect, depress, anx, adhd, opposit, conduct, stress, ravlt, fes_p, fes_y, trauma, maltr, first_d)
#correct for multiple comparisons using 'fdr' correction.
pvals<-pvals %>% mutate(q=p.adjust(p,method='fdr'),
                        sig=case_when(q<=0.05&q>0.01~"*",
                                      q<=0.01&q>0.001~"**",
                                      q<=0.001~"***",
                                      q>0.05~""))

#save
#save(pvals,file='data/2024114_4class_totalpvals_corrected.rdata')
#write.csv(pvals,file='outputs/20241114_4class_totalpvals_corrected.csv')
```

The p-column is the original p-value.  
The q-column is the corrected p-value.   
The sig column tells you if the q value is significant with asterisks ***.    
```{r}
pvals
```





# Read in Sleep

for post-hoc analysis 

## Dims
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/sleep/01_dims.out', header = FALSE ,skip=526,sep=" ")

dims<-data[c(2,14,26),c(5:ncol(data))]
dims<-data[c(2,14,26),c(5, 20, 26, 31, 37)]
dims<-dims %>% mutate(across(2:5,as.numeric))
colnames(dims)<-c("var",'est','se','t','p')


dims<-dims %>% mutate(class=c("1","2",'3'))
```

## SBD
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/sleep/02_sbd.out', header = FALSE ,skip=526,sep=" ")

sbd<-data[c(2,13,25),c(5:ncol(data))]
sbd<-data[c(2,13,25),c(5, 21, 27, 32, 33, 38)]
sbd<-sbd %>% mutate(across(2:6,as.numeric))

sbd$V32_33 <- c(11.014, 9.571, 2.658) 
sbd$NV38 <- c(0.000, 0.000, 0.008) # I checked this in the Mplus Out-file
sbd <- sbd[, !names(sbd) %in% c("V32", "V33", "V38")] # Remove the original columns


colnames(sbd)<-c("var",'est','se','t','p')
sbd<-sbd %>% mutate(class=c("1","2",'3'))

sbd
```

## DA
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/sleep/03_da.out', header = FALSE ,skip=526,sep=" ")

da<-data[c(2,13,24),c(5:ncol(data))]
da<-data[c(2,13,24),c(5, 22, 28, 33, 34, 39)]
da<-da %>% mutate(across(2:6,as.numeric))

da$V33_34 <- c(16.034, 11.759, 4.570) 
da$N39 <- sprintf("%.3f", c(0.000, 0.000, 0.000)) # I checked this in Mplus
da <- da[, !names(da) %in% c("V33", "V34", "V39")] # Remove the original columns


colnames(da)<-c("var",'est','se','t','p')
da<-da %>% mutate(class=c("1","2",'3'))

da
```

## SWTD
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/sleep/04_swtd.out', header = FALSE ,skip=526,sep=" ")

swtd<-data[c(2,14,26),c(5:ncol(data))]
swtd<-data[c(2,14,26),c(5, 20, 26, 31, 32, 37)]
swtd<-swtd %>% mutate(across(2:6,as.numeric))

swtd$V31_32 <- c(18.092, 17.016, 7.374) 
swtd$N37 <- sprintf("%.3f", c(0.000, 0.000, 0.000)) # I checked this in Mplus
swtd <- swtd[, !names(swtd) %in% c("V31", "V32", "V37")] # Remove the original columns


colnames(swtd)<-c("var",'est','se','t','p')
swtd<-swtd %>% mutate(class=c("1","2",'3'))

swtd
```

## DOES
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/sleep/05_does.out', header = FALSE ,skip=526,sep=" ")

does<-data[c(2,14,26),c(5:ncol(data))]
does<-data[c(2,14,26),c(5, 20, 26, 31, 32, 37)]
does<-does %>% mutate(across(2:6,as.numeric))

does$V31_32 <- c(12.204, 17.439, 8.216) 
does$N37 <- sprintf("%.3f", c(0.000, 0.000, 0.000)) # I checked this in Mplus
does <- does[, !names(does) %in% c("V31", "V32", "V37")] # Remove the original columns


colnames(does)<-c("var",'est','se','t','p')
does<-does %>% mutate(class=c("1","2",'3'))

does
```

## Shy
```{r}
data <- read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/sleep/06_shy.out', header = FALSE ,skip=526,sep=" ")

shy<-data[c(2,13,24),c(5:ncol(data))]
shy<-data[c(2,13,24),c(5, 21, 27, 33, 39)]
shy<-shy %>% mutate(across(2:5,as.numeric))
colnames(shy)<-c("var",'est','se','t','p')


shy<-shy %>% mutate(class=c("1","2",'3'))

shy
```



## Merge
```{r}
riskfactors_sleep = rbind(dims, sbd, da, swtd, does, shy)

#correct for multiple comparisons using 'fdr' correction.
riskfactors_sleep<-riskfactors_sleep %>% mutate(q=p.adjust(p,method='fdr'),
                        sig=case_when(q<=0.05&q>0.01~"*",
                                      q<=0.01&q>0.001~"**",
                                      q<=0.001~"***",
                                      q>0.05~""))
#the p-column is the original p-value
#the q-column is the corrected p-value
#the sig column tells you if the q value is significant with asterisks ***

#save
#save(riskfactors_sleep,file='data/2024114_pvalue_sleep_corrected.rdata')
#write.csv(riskfactors_sleep,file='outputs/20241114_pvalue_sleep_corrected.csv')
```

The p-column is the original p-value.  
The q-column is the corrected p-value.  
The sig column tells you if the q value is significant with asterisks ***.  

```{r}
riskfactors_sleep
```

# Demographics Only

### Sex
```{r}
data<-read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/without_covariates/01_sex.out', header=F,skip=519,sep=" ")   # skip rows before reading in data (check in Excel)

sex <- data[c(6,8,10), c(5,20:39)]
sex <- sex %>% remove_empty()

library(dplyr)
sex <- sex %>%
  mutate(across(c("V20", "V21", "V26", "V27", "V31", "V33", "V37", "V39", 
                  "V22", "V23", "V28", "V29", "V30", "V32", "V34", "V36"), as.numeric))


# Combine columns by removing NAs
sex$N1 <- ifelse(!is.na(sex$V20), sex$V20, sex$V21)
sex$N2 <- ifelse(!is.na(sex$V26), sex$V26, sex$V27)
sex$N3 <- ifelse(!is.na(sex$V31), sex$V31, sex$V33)
sex$N4 <- ifelse(!is.na(sex$V37), sex$V37, sex$V39)

# Remove the original columns
sex <- sex[, !names(sex) %in% c("V20", "V21", "V26", "V27", "V31", "V31", "V33", "V37", "V39", "V22", "V23", "V28", "V29", "V30", "V32", "V34", "V36", "V39")]
colnames(sex)<-c("var",'est','se','t','p')
sex <-sex %>% mutate(class=c("1","2",'3'))

sex
```

### Race
```{r}
## BLACK
data<-read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/without_covariates/02a_race_b.out', header=F,skip=529,sep=" ")   # skip rows before reading in data (check in Excel)
race_b <- data[c(3,5,7), c(5,15:36)]
race_b <- race_b %>% remove_empty()
race_b <- race_b[, !names(race_b) %in% c(paste0("V", 19:23), paste0("V", 27:29), paste0("V", 31:34))]
colnames(race_b)<-c("var",'est','se','t','p')
race_b <- race_b %>% mutate(class=c("1","2",'3'))

## American Indian/ Alaskan
data<-read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/without_covariates/02b_race_ai.out', header=F,skip=529,sep=" ")   # skip rows before reading in data (check in Excel)
race_ai <- data[c(3,5,7), c(5,17:35)]
race_ai <- race_ai %>% remove_empty()
race_ai <- race_ai[, !names(race_ai) %in% c(paste0("V", 18:22), paste0("V", 24:28), paste0("V", 30:34))]
colnames(race_ai)<-c("var",'est','se','t','p')
race_ai <- race_ai %>% mutate(class=c("1","2",'3'))

## Pacific
data<-read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/without_covariates/02c_race_p.out', header=F,skip=529,sep=" ")   # skip rows before reading in data (check in Excel)
race_p <- data[c(3,5,7), c(5,16:36)]
race_p <- race_p %>% mutate(across(V16:V36, as.numeric))
race_p <- race_p %>% remove_empty()
race_p <- race_p %>%
  mutate(
    N1 = coalesce(V16, V17, V18),
    N2 = coalesce(V22, V23, V24),
    N3 = coalesce(V26, V28, V30),
    N4 = coalesce(V32, V34, V36)
  )
race_p <- race_p[, !names(race_p) %in% c(paste0("V", 16:36))]
colnames(race_p)<-c("var",'est','se','t','p')
race_p <- race_p %>% mutate(class=c("1","2",'3'))

## Asian
data<-read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/without_covariates/02d_race_as.out', header=F,skip=529,sep=" ")   # skip rows before reading in data (check in Excel)
race_as <- data[c(3,5,7), c(5,16:34)]
race_as <- race_as %>% mutate(across(V16:V34, as.numeric))
race_as <- race_as %>% remove_empty()
colnames(race_as)<-c("var",'est','se','t','p')
race_as <- race_as %>% mutate(class=c("1","2",'3'))

## Other/ Multiple
data<-read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/without_covariates/02e_race_o.out', header=F,skip=529,sep=" ")   # skip rows before reading in data (check in Excel)
race_o <- data[c(3,5,7), c(5,18:36)]
race_o <- race_o %>% mutate(across(V18:V36, as.numeric))
race_o <- race_o %>% remove_empty()
colnames(race_o)<-c("var",'est','se','t','p')
race_o <- race_o %>% mutate(class=c("1","2",'3'))

race_o

race_as

race_b

race_ai

race_p
```

### Ethnicity
```{r}
data<-read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/without_covariates/03_ethn.out', header=F,skip=529,sep=" ")   # skip rows before reading in data (check in Excel)
ethn <- data[c(3,5,7), c(5,20:38)]
ethn <- ethn %>% mutate(across(V20:V38, as.numeric))
ethn <- ethn %>% remove_empty()
colnames(ethn)<-c("var",'est','se','t','p')
ethn <- ethn %>% mutate(class=c("1","2",'3'))

ethn
```

### Income-to-Needs
```{r}
data<-read.delim('E:/Masterarbeit/code/MPLUS/20241107_risk_predictors_NEW/without_covariates/04_inr.out', header=F,skip=529,sep=" ")   # skip rows before reading in data (check in Excel)
inr <- data[c(3,5,7), c(5,20:37)]
inr <- inr %>% mutate(across(V20:V37, as.numeric))
inr <- inr %>% remove_empty()
colnames(inr)<-c("var",'est','se','t','p')
inr <- inr %>% mutate(class=c("1","2",'3'))

inr
```


## Merge
```{r}
demographics_only = rbind(sex, race_ai, race_as, race_b, race_o, race_p, inr, ethn)

#correct for multiple comparisons using 'fdr' correction.
demographics_only<-demographics_only %>% mutate(q=p.adjust(p,method='fdr'),
                        sig=case_when(q<=0.05&q>0.01~"*",
                                      q<=0.01&q>0.001~"**",
                                      q<=0.001~"***",
                                      q>0.05~""))
#save
#save(demographics_only,file='data/20250213_pvalue_demographics_corrected.rdata')
#write.csv(demographics_only,file='outputs/20250213_pvalue_demographics_corrected.csv')
```

The p-column is the original p-value.  
The q-column is the corrected p-value.  
The sig column tells you if the q value is significant with asterisks ***.
```{r}
demographics_only
```


# OR-Table Risk Table - Main Analysis
```{r}
# Load Data
load("E:/Masterarbeit/data/riskfactors_with_covariates_FINAL.rdata") # ORs
load("E:/Masterarbeit/data/2024114_4class_totalpvals_corrected.rdata") # p-values

# Make "class" a factor, merge by class and var
pvals$class = as.factor(pvals$class)
riskfactors_with_covariates_FINAL$class = as.factor(riskfactors_with_covariates_FINAL$class)
table<-inner_join(riskfactors_with_covariates_FINAL,pvals) # Joining with `by = join_by(var, class)`



#remove the 99th & 90th percentiles, and cohen's d values, and round variables to 3 decimal places
tab1<-table %>% 
  select(!c(contains("99"),contains("90"),contains("_d"),est,se,t)) %>%
  mutate(across(lower_95:upper_95,~round(.x,2)),
         q=round(q,3))

#create merged 95% CI column
tab1<-tab1 %>% unite(CI_95,c('lower_95','upper_95'),sep='-') %>%
  select(var,class,OR,CI_95,p,q,sig)

#pivot rows to columns
tab2<-tab1 %>% pivot_wider(names_from=class,values_from=c('OR','CI_95','p','q','sig'))

#select only variables you want (odds ratio class 1, 95% CI class 1, sig class 1; odds ratio class 2, 95% CI class 2, sig class 2 and so on)
#also include q variable for each class if you wish
tab2<-tab2 %>% select(var,contains('OR_1'),contains('CI_95_1'),contains('q_1'), contains('sig_1'),
                      contains('OR_2'),contains('CI_95_2'),contains('q_2'), contains('sig_2'),
                      contains('OR_3'),contains('CI_95_3'),contains('q_3'), contains('sig_3'))
tab2<-tab2 %>% mutate(var=case_when(var=='SLEEP'~"Sleep Disturbances",
                                    var=="IBS"~'Irritable Bowel Symptoms',
                                    var=="ASTHMA"~'Asthma',
                                    var=="BMI"~"BMI",
                                    var=="PREG"~'Pregnancy Complications',
                                    var=='OBST'~'Obstetric Complications',
                                    var=='PREMAT'~'Premature Birth',
                                    var=='SMALL'~'Small at Birth',
                                    var=='CSECT'~"C-Section",
                                    var=='DEPRESS'~"Depression",
                                    var=='ANX'~"Anxiety",
                                    var=='ADHD'~"ADHD", 
                                    var=='OPPOSIT'~"Oppositional Defiant Symptoms",
                                    var=="CONDUCT"~"Conduct Symptoms",
                                    var=="STRESS"~"Stress",
                                    var=='RAVLT'~'Verbal Learning',
                                    var=='FES_P'~'Family Conflict - Parent',
                                    var=='FES_Y'~'Family Conflict - Youth',
                                    var=='TRAUMA'~'Trauma',
                                    var=='MALTR'~'Maltreatment',
                                    var=='FIRST_D'~'First-Degree Relatives'))


#merge sig *** and ORs together with unite() command
tab3<-tab2 %>% unite(OR_1,c('OR_1','sig_1'),sep='') %>%
  unite(`OR_2`,c('OR_2','sig_2'),sep='') %>%
  unite(`OR_3`,c('OR_3','sig_3'),sep='')
tab3 <- tab3 %>% select(-q_1, -q_2, -q_3)

#save table3 as a csv
#write.csv(tab3,file="E:/Masterarbeit/outputs/20241114_short_ORtable.csv",row.names=F)
#write.csv(tab2,file="E:/Masterarbeit/outputs/20241114_long_ORtable.csv",row.names=F)

# save it as a table - long table
#library(flextable)
#library(officer)
#table <- flextable(tab2)
#doc <- read_docx() %>%
#  body_add_flextable(table)
#print(doc, target = "E:/Masterarbeit/outputs/OR_p_table.docx")

# save it as a table - short table
#table <- flextable(tab3)
#doc <- read_docx() %>%
#  body_add_flextable(table)
#print(doc, target = "E:/Masterarbeit/outputs/OR_p_table_short.docx")
```

Let's examine the long table. For a clearer view, refer to Table 2 in my Master's thesis—it's the same table. I used the more concise version (tab3) for simplicity.

```{r}
tab2
```

Let's examine the short table. For a clearer view, refer to Table 2 in my Master's thesis—it's the exact same table!

```{r}
tab3
```


# OR Risk Table - Sleep
```{r}
load("data/riskfactors_sleep_FINAL.rdata") # ORs
load("data/2024114_pvalue_sleep_corrected.rdata") # p-values

# Make "class" a factor, merge by class and var
riskfactors_sleep$class = as.factor(riskfactors_sleep$class)
riskfactors_sleep_FINAL$class = as.factor(riskfactors_sleep_FINAL$class)
table<-inner_join(riskfactors_sleep,riskfactors_sleep_FINAL) # Joining with `by = join_by(var, class)`



#remove the 99th & 90th percentiles, and cohen's d values, and round variables to 3 decimal places
tab1<-table %>% 
  select(!c(contains("99"),contains("90"),contains("_d"),est,se,t)) %>%
  mutate(across(lower_95:upper_95,~round(.x,2)),
         q=round(q,3))

#create merged 95% CI column
tab1<-tab1 %>% unite(CI_95,c('lower_95','upper_95'),sep='-') %>%
  select(var,class,OR,CI_95,p,q,sig)

#pivot rows to columns
tab2<-tab1 %>% pivot_wider(names_from=class,values_from=c('OR','CI_95','p','q','sig'))

#select only variables you want (odds ratio class 1, 95% CI class 1, sig class 1; odds ratio class 2, 95% CI class 2, sig class 2 and so on)
#also include q variable for each class if you wish
tab2<-tab2 %>% select(var,contains('OR_1'),contains('CI_95_1'),contains('q_1'), contains('sig_1'),
                      contains('OR_2'),contains('CI_95_2'),contains('q_2'), contains('sig_2'),
                      contains('OR_3'),contains('CI_95_3'),contains('q_3'), contains('sig_3'))
tab2<-tab2 %>% mutate(var=case_when(var=='DIMS'~"Disorders of Initiating and Maintaining Sleep",
                                    var=="SBD"~'Sleep Breathing Disorders',
                                    var=="DA"~'Disorder of Arousal ',
                                    var=="SWTD"~"Sleep-Wake transition Disorders",
                                    var=="DOES"~'Disorders of Excessive Somnolence',
                                    var=='SHY'~'Sleep Hyperhydrosis'))


#merge sig *** and ORs together with unite() command
tab3<-tab2 %>% unite(OR_1,c('OR_1','sig_1'),sep='') %>%
  unite(`OR_2`,c('OR_2','sig_2'),sep='') %>%
  unite(`OR_3`,c('OR_3','sig_3'),sep='')
tab3 <- tab3 %>% select(-q_1, -q_2, -q_3)

#save table2 and table3 as a csv
#write.csv(tab3,file="E:/Masterarbeit/outputs/20241114_short_ORtable_SLEEP.csv",row.names=F)
#write.csv(tab2,file="E:/Masterarbeit/outputs/20241114_long_ORtable_SLEEP.csv",row.names=F)

# save it as a table - long table
#library(flextable)
#library(officer)
#table <- flextable(tab2)
#doc <- read_docx() %>%
#  body_add_flextable(table)
#print(doc, target = "E:/Masterarbeit/outputs/OR_p_table_long_SLEEP.docx")

# save it as a table - short table
#table <- flextable(tab3)
#doc <- read_docx() %>%
#  body_add_flextable(table)
#print(doc, target = "E:/Masterarbeit/outputs/OR_p_table_short_SLEEP.docx")
```

Let's examine the long table. For a clearer view, refer to Supplemental Table 5 in my Master's  — it's the same table. I used the more concise version (tab3) for simplicity.

```{r}
tab2
```

Let's examine the short table. For a clearer view, refer to Supplemental Table 5 in my Master's  — it's the exact same table. 

```{r}
tab3
```

# OR risk table demographics only
```{r}
load("data/demographics_without_covariates_FINAL.rdata") # ORs
load("data/20250213_pvalue_demographics_corrected.rdata") # p-values

# Make "class" a factor, merge by class and var
demographics_without_covariates_FINAL$class = as.factor(demographics_without_covariates_FINAL$class)
demographics_only$class = as.factor(demographics_only$class)
table<-inner_join(demographics_without_covariates_FINAL,demographics_only) # Joining with `by = join_by(var, class)`



#remove the 99th & 90th percentiles, and cohen's d values, and round variables to 3 decimal places
tab1<-table %>% 
  select(!c(contains("99"),contains("90"),contains("_d"),est,se,t)) %>%
  mutate(across(lower_95:upper_95,~round(.x,2)),
         q=round(q,3))

#create merged 95% CI column
tab1<-tab1 %>% unite(CI_95,c('lower_95','upper_95'),sep='-') %>%
  select(var,class,OR,CI_95,p,q,sig)

#pivot rows to columns
tab2<-tab1 %>% pivot_wider(names_from=class,values_from=c('OR','CI_95','p','q','sig'))

#select only variables you want (odds ratio class 1, 95% CI class 1, sig class 1; odds ratio class 2, 95% CI class 2, sig class 2 and so on)
#also include q variable for each class if you wish
tab2<-tab2 %>% select(var,contains('OR_1'),contains('CI_95_1'),contains('q_1'), contains('sig_1'),
                      contains('OR_2'),contains('CI_95_2'),contains('q_2'), contains('sig_2'),
                      contains('OR_3'),contains('CI_95_3'),contains('q_3'), contains('sig_3'))

tab2<-tab2 %>% mutate(var=case_when(var=='SEX'~"Sex",
                                    var=="RACE_B"~'Race: Black',
                                    var=="RACE_AS"~'Race: Asian',
                                    var=="RACE_P"~"Race: Pacific",
                                    var=="RACE_AI"~'Race: American Indian/Alaskan',
                                    var=="RACE_O"~'Race: Other/Multiple',
                                    var=='INR'~'Socioeconomic Status',
                                    var=='ETHN'~'Hispanic Ethnicity'))


#merge sig *** and ORs together with unite() command
tab3<-tab2 %>% unite(OR_1,c('OR_1','sig_1'),sep='') %>%
  unite(`OR_2`,c('OR_2','sig_2'),sep='') %>%
  unite(`OR_3`,c('OR_3','sig_3'),sep='')
tab3 <- tab3 %>% select(-q_1, -q_2, -q_3)

#save table2 and table3 as a csv
#write.csv(tab3,file="E:/Masterarbeit/outputs/20250213_short_ORtable_DEMOGRAPHICS.csv",row.names=F)
#write.csv(tab2,file="E:/Masterarbeit/outputs/20250213_long_ORtable_DEMOGRAPHICS.csv",row.names=F)

# save it as a table - long table
#library(flextable)
#library(officer)
#table <- flextable(tab2)
#doc <- read_docx() %>%
#  body_add_flextable(table)
#print(doc, target = "E:/Masterarbeit/outputs/OR_p_table_long_DEMORAPHICS.docx")

# save it as a table - short table
#table <- flextable(tab3)
#doc <- read_docx() %>%
#  body_add_flextable(table)
#print(doc, target = "E:/Masterarbeit/outputs/OR_p_table_short_DEMOGRAPHICS.docx")
```

Let's examine the long table. For a clearer view, refer to Table 2 in my Master's  — it's the same table. I used the more concise version (tab3) for simplicity.

```{r}
tab2
```

Let's examine the short table. For a clearer view, refer to Table 2 in my Master's  — it's the exact same table.

```{r}
tab3
```