---
title: "Mania_Modelling"
author: "by_Jasmin_Doenicke"
date: "Step 10"
output:
  html_document:
    toc: yes
    theme: united
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---

This script generates plots showing individual trajectories of mania symptoms across visits, and portrays the effects of risk factors.  
The "perfect" plots were chosen for the manuscript (e.g. Figure 1, Figure 2), so this code demonstrates me trying out different options.  

# STARTER Code
```{r}
#libraries
library(tidyverse)
library(MplusAutomation)
library(vtable)
library(flextable)
library(viridis)
library(ggpubr)
library(grid)

setwd("E:/Masterarbeit")
knitr::opts_knit$set(root.dir = "E:/Masterarbeit")

#load data
load(file='data/GBI_demographics.rdata')

##Set theme
theme_set(theme_bw())

load(file='data/GBI_demographics.rdata') #demographic data

#read input for ids (data4tp_id)
data_csv<-read.csv('E:/Masterarbeit/code/MPLUS/data_headers.csv',
                   header=T)

model_L4<-readModels('E:/Masterarbeit/code/MPLUS/neg_binomial_FIXED/03_linear_4class.out',
what=c("savedata"))$savedata

table(model_L4$C) # check class distribution, reorder from smallest to biggest

#merge with id data
merge_csv<-cbind(data_csv,model_L4)
merge_csv<-merge_csv %>% rename(class=C) %>% select(src_subject_id,class)
merge<-inner_join(GBI_demographics,merge_csv)

# clean up environment
rm(data_csv, GBI_demographics, merge_csv, model_L4)
```


# PLOT1 
## 5 Plot Lineplot -  Separate Plots
```{r}
plot1 = merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.25) +  # Decreased opacity of individual lines
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), linewidth = 2) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, max(merge$pgbi_p_ss_score, na.rm = TRUE), by = 5)) +  # Custom y-axis ticks
  scale_color_manual(
    values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[4], '4' = viridis(10)[1]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")
      #theme(legend.title=element_blank()),
    #guide = "none" # remove legend
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[4], '4' = viridis(10)[1]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None"),
    guide = "none" # disable separate legend for fill
  ) +
  xlab("") +
  ylab("") +
  theme_minimal() +  # Use a minimal theme
  theme(
    panel.grid = element_blank(),  # Remove all gridlines
    panel.border = element_rect(color = "black", fill = NA)  # Add the outline back
  )


#ggsave("CB_4class_total_individual_3_tall.jpg", plot = plot1, width = 10, height = 7, dpi = 300, units = "in")
#ggsave("CB_4class_total_individual_3_regular.jpg", plot = plot1, width = 10, height = 6, dpi = 300, units = "in")
#ggsave("CB_4class_total_individual_3_wide.jpg", plot = plot1, width = 10, height = 5, dpi = 300, units = "in")

plot1
```


```{r}
plot2 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '1') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.25, color = viridis(10)[10]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[10], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
  scale_color_manual(
    values = c('1' = viridis(10)[10]),
    labels = c('1' = "High"),
    guide = "none" # remove legend
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[10]),
    labels = c('1' = "High mania symptoms (575, 5%)"),
    guide = "none" # disable separate legend for fill
  ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),  # Remove gridlines
    panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
    legend.position = ("top"),  # Correct legend position inside the plot
    legend.title = element_blank()  # Remove legend title)
    #legend.text = element_text(size = 12),  # Increase the size of legend text
    #legend.key.size = unit(1.5, "lines")  # Increase the size of legend keys
)

# ggsave("CB_4class_CL1_tall.jpg", plot = plot2, width = 10, height = 7, dpi = 300, units = "in")
# ggsave("CB_4class_CL1_regular.jpg", plot = plot2, width = 10, height = 6, dpi = 300, units = "in")
# ggsave("CB_4class_CL1_wide.jpg", plot = plot2, width = 10, height = 5, dpi = 300, units = "in")

plot2
```


```{r}
plot3 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '2') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.02, color = viridis(10)[8]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[8], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
    scale_color_manual(
    values = c('2' = viridis(10)[8]),
    labels = c('2' = "Moderate"),
    guide = "none" # remove legend
  )+
  scale_fill_manual(
    values = c('2' = viridis(10)[8]),
    labels = c('2' = "Moderate mania symptoms (1631, 15%)"),
    guide = "none" # disable separate legend for fill
  ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),  # Remove gridlines
    panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
    legend.position = ("top"),  # Correct legend position inside the plot
    legend.title = element_blank()  # Remove legend title)
    #legend.text = element_text(size = 12),  # Increase the size of legend text
    #legend.key.size = unit(1.5, "lines")  # Increase the size of legend keys
)

plot3
```


```{r}
plot4 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '3') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.02, color = viridis(10)[5]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[5], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
    scale_color_manual(
    values = c('3' = viridis(10)[5]),
    labels = c('3' = "Low"),
    guide = "none" # remove legend
  )+
  scale_fill_manual(
    values = c('3' = viridis(10)[5]),
    labels = c('3' = "Low mania symptoms (3227, 30%)"),
    guide = "none" # disable separate legend for fill
  ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),  # Remove gridlines
    panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
    legend.position = ("top"),  # Correct legend position inside the plot
    legend.title = element_blank()  # Remove legend title)
    #legend.text = element_text(size = 12),  # Increase the size of legend text
    #legend.key.size = unit(1.5, "lines")  # Increase the size of legend keys
)

plot4
```

```{r}
plot5 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '4') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.005, color = viridis(10)[1]) +  # Match color to geom_smooth, alpha = how opaque
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[1], linewidth = 0.01) +
  geom_segment(aes(x = 0, xend = 2, y = 0, yend = 0), color = viridis(10)[1], size = 0.8, alpha = 0.05) + # add line
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
  scale_color_manual(
    values = c('4' = viridis(10)[1]),  # Ensure levels match `class`
    labels = c('4' = "None"),
    guide = "none" # remove legend
  ) +
  scale_fill_manual(
    values = c('4' = viridis(10)[1]),  # Ensure levels match `class`
    labels = c('4' = "No mania symptoms (5201, 49%)"),
    guide = "none" # remove legend
  ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),  # Remove gridlines
    panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
    legend.position = ("top"),  # Correct legend position inside the plot
    legend.title = element_blank()  # Remove legend title)
    #legend.text = element_text(size = 12),  # Increase the size of legend text
    #legend.key.size = unit(1.5, "lines")  # Increase the size of legend keys
)

plot5
```

## 5 Plot Lineplot - Together
```{r}
plot1 = merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.035) +  # Decreased opacity of individual lines
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class)) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, max(merge$pgbi_p_ss_score, na.rm = TRUE), by = 5)) +  # Custom y-axis ticks
  scale_color_manual(
    values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[4], '4' = viridis(10)[1]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")+
      theme(legend.title=element_blank()),
    guide = "none" # remove legend
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[4], '4' = viridis(10)[1]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None"),
    guide = "none" # disable separate legend for fill
  ) +
  xlab("") +
  ylab("") +
  theme_minimal() +  # Use a minimal theme
  theme(
    panel.grid = element_blank(),  # Remove all gridlines
    panel.border = element_rect(color = "black", fill = NA)  # Add the outline back
  )


plot2 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '1') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.05, color = viridis(10)[10]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[10], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
  scale_color_manual(
    values = c('1' = viridis(10)[10]),
    labels = c('1' = "High"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[10]),
    labels = c('1' = "High symptoms (575, 5%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),  # Remove gridlines
    panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
    legend.position = c(0.5, 0.90),  # Legend at the top middle
    legend.direction = "horizontal",  # Horizontal orientation for legend
    legend.text = element_text(size = 6),  # Set legend text size
    legend.key.size = unit(1, "lines")  # Adjust legend key size
  )



plot3 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '2') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.02, color = viridis(10)[8]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[8], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
    scale_color_manual(
    values = c('2' = viridis(10)[8]),
    labels = c('2' = "Moderate"),
    guide = guide_legend(title = NULL) # remove legend title
  )+
  scale_fill_manual(
    values = c('2' = viridis(10)[8]),
    labels = c('2' = "Moderate symptoms (1631, 15%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),  # Remove gridlines
    panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
    legend.position = c(0.5, 0.90),  # Legend at the top middle
    legend.direction = "horizontal",  # Horizontal orientation for legend
    legend.text = element_text(size = 4.5),  # Set legend text size
    legend.key.size = unit(1, "lines")  # Adjust legend key size
  )


plot4 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '3') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.02, color = viridis(10)[5]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[5], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
    scale_color_manual(
    values = c('3' = viridis(10)[5]),
    labels = c('3' = "Low"),
    guide = guide_legend(title = NULL)
  )+
  scale_fill_manual(
    values = c('3' = viridis(10)[5]),
    labels = c('3' = "Low symptoms (3227, 30%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),  # Remove gridlines
    panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
    legend.position = c(0.5, 0.90),  # Legend at the top middle
    legend.direction = "horizontal",  # Horizontal orientation for legend
    legend.text = element_text(size = 4.5),  # Set legend text size
    legend.key.size = unit(1, "lines")  # Adjust legend key size
  )


plot5 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '4') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.005, color = viridis(10)[1]) +  # Match color to geom_smooth, alpha = how opaque
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[1], linewidth = 0.8) +
  geom_segment(aes(x = 0, xend = 2, y = 0, yend = 0), color = viridis(10)[1], size = 0.8, alpha = 0.05) + # add line
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
  scale_color_manual(
    values = c('4' = viridis(10)[1]),  # Ensure levels match `class`
    labels = c('4' = "None"),
    guide = guide_legend(title = NULL)
  ) +
  scale_fill_manual(
    values = c('4' = viridis(10)[1]),  # Ensure levels match `class`
    labels = c('4' = "No symptoms (5201, 49%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),  # Remove gridlines
    panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
    legend.position = c(0.5, 0.90),  # Legend at the top middle
    legend.direction = "horizontal",  # Horizontal orientation for legend
    legend.text = element_text(size = 4.5),  # Set legend text size
    legend.key.size = unit(1, "lines")  # Adjust legend key size
  )

```

### add plots
```{r}
# Alternative 1
library(ggpubr)
plot6 = ggarrange(plot1, plot2, plot3, plot4, plot5, ncol = 5, nrow = 1)
#ggsave("CB_5plot_tall_5.jpg", plot = plot6, width = 10, height = 4, dpi = 300, units = "in")
# ggsave("CB_5plot_regular_5.jpg", plot = plot6, width = 10, height = 3, dpi = 300, units = "in")
# ggsave("CB_5plot_wide_5.jpg", plot = plot6, width = 10, height = 2, dpi = 300, units = "in")

plot6
```


```{r}
plot7 = annotate_figure(plot6, left = textGrob("Total score", rot = 90, vjust = 1, gp = gpar(cex = 1)), bottom = textGrob("Visit", gp = gpar(cex = 1)))
# ggsave("CB_5plot_tall_6.jpg", plot = plot7, width = 10, height = 4, dpi = 300, units = "in")
# ggsave("CB_5plot_regular_6.jpg", plot = plot7, width = 10, height = 3, dpi = 300, units = "in")
# ggsave("CB_5plot_wide_6.jpg", plot = plot7, width = 10, height = 2, dpi = 300, units = "in")

plot7
```

## 5 Plot Lineplot - Together - Small Changes
```{r}
plot1 = merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.035) +  # Decreased opacity of individual lines
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class)) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, max(merge$pgbi_p_ss_score, na.rm = TRUE), by = 5)) +  # Custom y-axis ticks
  scale_color_manual(
    values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[4], '4' = viridis(10)[1]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")+
      theme(legend.title=element_blank()),
    guide = "none" # remove legend
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[4], '4' = viridis(10)[1]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None"),
    guide = "none" # disable separate legend for fill
  ) +
  xlab("") +
  ylab("") +
  theme_minimal() +  # Use a minimal theme
  theme(
    panel.grid = element_blank(),  # Remove all gridlines
    panel.border = element_rect(color = "black", fill = NA)  # Add the outline back
  )


plot2 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '1') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.05, color = viridis(10)[10]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[10], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
  scale_color_manual(
    values = c('1' = viridis(10)[10]),
    labels = c('1' = "High"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[10]),
    labels = c('1' = "High symptoms (575, 5%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = c(0.5, 0.90),  # Legend at the top middle
  legend.direction = "horizontal",  # Horizontal orientation for legend
  legend.box = "horizontal",  # Allow wrapping to the next row
  legend.text = element_text(size = 6)  # Set consistent text size
  )



plot3 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '2') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.02, color = viridis(10)[8]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[8], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
    scale_color_manual(
    values = c('2' = viridis(10)[8]),
    labels = c('2' = "Moderate"),
    guide = guide_legend(title = NULL) # remove legend title
  )+
  scale_fill_manual(
    values = c('2' = viridis(10)[8]),
    labels = c('2' = "Moderate symptoms \n (1631, 15%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = c(0.5, 0.90),  # Legend at the top middle
  legend.direction = "horizontal",  # Horizontal orientation for legend
  legend.box = "horizontal",  # Allow wrapping to the next row
  legend.text = element_text(size = 6)  # Set consistent text size
  )

plot4 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '3') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.02, color = viridis(10)[5]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[5], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
    scale_color_manual(
    values = c('3' = viridis(10)[5]),
    labels = c('3' = "Low"),
    guide = guide_legend(title = NULL)
  )+
  scale_fill_manual(
    values = c('3' = viridis(10)[5]),
    labels = c('3' = "Low symptoms (3227, 30%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = c(0.5, 0.90),  # Legend at the top middle
  legend.direction = "horizontal",  # Horizontal orientation for legend
  legend.box = "horizontal",  # Allow wrapping to the next row
  legend.text = element_text(size = 6),  # Set consistent text size
  legend.key.size = unit(1, "lines")  # Adjust legend key size
)


plot5 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '4') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.005, color = viridis(10)[1]) +  # Match color to geom_smooth, alpha = how opaque
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[1], linewidth = 0.8) +
  geom_segment(aes(x = 0, xend = 2, y = 0, yend = 0), color = viridis(10)[1], size = 0.8, alpha = 0.05) + # add line
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
  scale_color_manual(
    values = c('4' = viridis(10)[1]),  # Ensure levels match `class`
    labels = c('4' = "None"),
    guide = guide_legend(title = NULL)
  ) +
  scale_fill_manual(
    values = c('4' = viridis(10)[1]),  # Ensure levels match `class`
    labels = c('4' = "No symptoms (5201, 49%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = c(0.5, 0.90),  # Legend at the top middle
  legend.direction = "horizontal",  # Horizontal orientation for legend
  legend.box = "horizontal",  # Allow wrapping to the next row
  legend.text = element_text(size = 6),  # Set consistent text size
  legend.key.size = unit(1, "lines")  # Adjust legend key size
)

```

### add plots
```{r}
# Alternative 1
plot6 = ggarrange(plot1, plot2, plot3, plot4, plot5, ncol = 5, nrow = 1)
plot7 = annotate_figure(plot6, left = textGrob("Total score", rot = 90, vjust = 1, gp = gpar(cex = 1)), bottom = textGrob("Visit", gp = gpar(cex = 1)))

# ggsave("CB_5plot_wide_11.jpg", plot = plot7, width = 10, height = 2, dpi = 300, units = "in")
# ggsave("CB_5plot_tall_11.jpg", plot = plot7, width = 10, height = 4, dpi = 300, units = "in")
# ggsave("CB_5plot_regular_11.jpg", plot = plot7, width = 10, height = 3, dpi = 300, units = "in")

plot6
```

## FINAL PLOT1 - switched color
```{r}
plot1 = merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.035) +  # Decreased opacity of individual lines
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class)) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, max(merge$pgbi_p_ss_score, na.rm = TRUE), by = 5)) +  # Custom y-axis ticks
  scale_color_manual(
    values = c('1' = viridis(10)[1], '2' = viridis(10)[4], '3' = viridis(10)[8], '4' = viridis(10)[10]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")+
      theme(legend.title=element_blank()),
    guide = "none" # remove legend
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[1], '2' = viridis(10)[4], '3' = viridis(10)[8], '4' = viridis(10)[10]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None"),
    guide = "none" # disable separate legend for fill
  ) +
  xlab("") +
  ylab("") +
  theme_minimal() +  # Use a minimal theme
  theme(
    panel.grid = element_blank(),  # Remove all gridlines
    panel.border = element_rect(color = "black", fill = NA)  # Add the outline back
  )


plot2 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '1') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.05, color = viridis(10)[1]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[1], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
  scale_color_manual(
    values = c('1' = viridis(10)[1]),
    labels = c('1' = "High"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[1]),
    labels = c('1' = "High symptoms (575, 5%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = c(0.5, 0.90),  # Legend at the top middle
  legend.direction = "horizontal",  # Horizontal orientation for legend
  legend.box = "horizontal",  # Allow wrapping to the next row
  legend.text = element_text(size = 6)  # Set consistent text size
  )



plot3 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '2') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.02, color = viridis(10)[4]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[4], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
    scale_color_manual(
    values = c('2' = viridis(10)[4]),
    labels = c('2' = "Moderate"),
    guide = guide_legend(title = NULL) # remove legend title
  )+
  scale_fill_manual(
    values = c('2' = viridis(10)[4]),
    labels = c('2' = "Moderate symptoms \n (1631, 15%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = c(0.5, 0.89),  # Legend at the top middle
  legend.direction = "horizontal",  # Horizontal orientation for legend
  legend.box = "horizontal",  # Allow wrapping to the next row
  legend.text = element_text(size = 6)  # Set consistent text size
  )

plot4 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '3') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.02, color = viridis(10)[8]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[8], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
    scale_color_manual(
    values = c('3' = viridis(10)[8]),
    labels = c('3' = "Low"),
    guide = guide_legend(title = NULL)
  )+
  scale_fill_manual(
    values = c('3' = viridis(10)[8]),
    labels = c('3' = "Low symptoms (3227, 30%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = c(0.5, 0.90),  # Legend at the top middle
  legend.direction = "horizontal",  # Horizontal orientation for legend
  legend.box = "horizontal",  # Allow wrapping to the next row
  legend.text = element_text(size = 6),  # Set consistent text size
  legend.key.size = unit(1, "lines")  # Adjust legend key size
)


plot5 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '4') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.005, color = viridis(10)[10]) +  # Match color to geom_smooth, alpha = how opaque
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[10], linewidth = 0.8) +
  geom_segment(aes(x = 0, xend = 2, y = 0, yend = 0), color = viridis(10)[10], size = 0.8, alpha = 0.05) + # add line
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
  scale_color_manual(
    values = c('4' = viridis(10)[10]),  # Ensure levels match `class`
    labels = c('4' = "None"),
    guide = guide_legend(title = NULL)
  ) +
  scale_fill_manual(
    values = c('4' = viridis(10)[10]),  # Ensure levels match `class`
    labels = c('4' = "No symptoms (5201, 49%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = c(0.5, 0.90),  # Legend at the top middle
  legend.direction = "horizontal",  # Horizontal orientation for legend
  legend.box = "horizontal",  # Allow wrapping to the next row
  legend.text = element_text(size = 6),  # Set consistent text size
  legend.key.size = unit(1, "lines")  # Adjust legend key size
)

```

### add plots
```{r}
# Alternative 1
library(ggpubr)
library(grid)
plot6 = ggarrange(plot1, plot2, plot3, plot4, plot5, ncol = 5, nrow = 1)
plot7 = annotate_figure(plot6, left = textGrob("Total score", rot = 90, vjust = 1, gp = gpar(cex = 1)),
                    bottom = textGrob("Visit", gp = gpar(cex = 1)))

# ggsave("CB_5plot_wide_12.jpg", plot = plot7, width = 10, height = 2, dpi = 300, units = "in")
# ggsave("CB_5plot_tall_12.jpg", plot = plot7, width = 10, height = 4, dpi = 300, units = "in")
# ggsave("CB_5plot_regular_12.jpg", plot = plot7, width = 10, height = 3, dpi = 300, units = "in")

plot7
```

## FINAL FINAL PLOT - 1 column
```{r}
plot1 = merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.035) +  # Decreased opacity of individual lines
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class)) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, max(merge$pgbi_p_ss_score, na.rm = TRUE), by = 5)) +  # Custom y-axis ticks
  scale_color_manual(
    values = c('1' = viridis(10)[1], '2' = viridis(10)[4], '3' = viridis(10)[8], '4' = viridis(10)[10]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")+
      theme(legend.title=element_blank()),
    guide = "none" # remove legend
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[1], '2' = viridis(10)[4], '3' = viridis(10)[8], '4' = viridis(10)[10]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None"),
    guide = "none" # disable separate legend for fill
  ) +
  xlab("Visit") +
  ylab("") +
  theme_minimal() +  # Use a minimal theme
  theme(
    panel.grid = element_blank(),  # Remove all gridlines
    panel.border = element_rect(color = "black", fill = NA)  # Add the outline back
  )


plot2 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '1') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.05, color = viridis(10)[1]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[1], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
  scale_color_manual(
    values = c('1' = viridis(10)[1]),
    labels = c('1' = "High"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[1]),
    labels = c('1' = "High symptoms (575, 5%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = c(0.5, 0.90),  # Legend at the top middle
  legend.direction = "horizontal",  # Horizontal orientation for legend
  legend.box = "horizontal",  # Allow wrapping to the next row
  legend.text = element_text(size = 12),  # Set consistent text size
  legend.key.size = unit(1, "lines")  # Adjust legend key size
  )



plot3 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '2') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.02, color = viridis(10)[4]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[4], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
    scale_color_manual(
    values = c('2' = viridis(10)[4]),
    labels = c('2' = "Moderate"),
    guide = guide_legend(title = NULL) # remove legend title
  )+
  scale_fill_manual(
    values = c('2' = viridis(10)[4]),
    labels = c('2' = "Moderate symptoms (1631, 15%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = c(0.5, 0.89),  # Legend at the top middle
  legend.direction = "horizontal",  # Horizontal orientation for legend
  legend.box = "horizontal",  # Allow wrapping to the next row
  legend.text = element_text(size = 12),  # Set consistent text size
  legend.key.size = unit(1, "lines")  # Adjust legend key size
  )

plot4 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '3') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.02, color = viridis(10)[8]) +  # Match color to geom_smooth
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[8], linewidth = 0.8) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
    scale_color_manual(
    values = c('3' = viridis(10)[8]),
    labels = c('3' = "Low"),
    guide = guide_legend(title = NULL)
  )+
  scale_fill_manual(
    values = c('3' = viridis(10)[8]),
    labels = c('3' = "Low symptoms (3227, 30%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("") +
  ylab("") +
  theme_minimal() +
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = c(0.5, 0.90),  # Legend at the top middle
  legend.direction = "horizontal",  # Horizontal orientation for legend
  legend.box = "horizontal",  # Allow wrapping to the next row
  legend.text = element_text(size = 12),  # Set consistent text size
  legend.key.size = unit(1, "lines")  # Adjust legend key size
)


plot5 <- merge %>%
  mutate(class = factor(class)) %>%
  filter(!c(visit == "3" | visit == "4")) %>%
  filter(class == '4') %>%
  ggplot(aes(y = pgbi_p_ss_score, x = visit, color = class, fill = class)) +
  geom_line(aes(group = src_subject_id), alpha = 0.005, color = viridis(10)[10]) +  # Match color to geom_smooth, alpha = how opaque
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class), color = viridis(10)[10], linewidth = 0.8) +
  geom_segment(aes(x = 0, xend = 2, y = 0, yend = 0), color = viridis(10)[10], size = 0.8, alpha = 0.05) + # add line
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), limits = c(0, 30)) +  # Define y-axis scale
  scale_color_manual(
    values = c('4' = viridis(10)[10]),  # Ensure levels match `class`
    labels = c('4' = "None"),
    guide = guide_legend(title = NULL)
  ) +
  scale_fill_manual(
    values = c('4' = viridis(10)[10]),  # Ensure levels match `class`
    labels = c('4' = "No symptoms (5201, 49%)"),
    guide = guide_legend(title = NULL) # Add legend with title as NULL
 ) +
  xlab("Visit") +
  ylab("") +
  theme_minimal() +
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = c(0.5, 0.90),  # Legend at the top middle
  legend.direction = "horizontal",  # Horizontal orientation for legend
  legend.box = "horizontal",  # Allow wrapping to the next row
  legend.text = element_text(size = 12),  # Set consistent text size
  legend.key.size = unit(1, "lines"),  # Adjust legend key size
   axis.title.x = element_text(size = 16)  # Make the x-axis label bigger
)

```

### add plots
```{r}
library(ggpubr)
library(grid)
plot6 = ggarrange(plot2, plot3, plot4, plot5, ncol = 1, nrow = 4)
plot7 = annotate_figure(plot6, left = textGrob("Total mania score", rot = 90, vjust = 1, gp = gpar(cex = 1.5)))

# ggsave("CB_5plot_1C_wide_9.jpg", plot = plot7, width = 5, height = 10, dpi = 300, units = "in")
# ggsave("CB_5plot_1C_tall_9.jpg", plot = plot7, width = 5, height = 12, dpi = 300, units = "in")
# ggsave("CB_5plot_1C_regular_9.jpg", plot = plot7, width = 5, height = 11, dpi = 300, units = "in")

plot7
```


```{r}
# save plot 1 single
ggsave("CB_P1_wide_9.jpg", plot = plot1, width = 5, height = 8, dpi = 300, units = "in")
ggsave("CB_P1_tall_9.jpg", plot = plot1, width = 5, height = 10, dpi = 300, units = "in")
ggsave("CB_P1_regular_9.jpg", plot = plot1, width = 5, height = 12, dpi = 300, units = "in")

plot1
# Perfect combo: CB_5plot_1C_tall_9, CB_P1_wide_9
 ggsave("FINAL_CB_5plot_1C_tall_9_HD.jpg", plot = plot7, width = 5, height = 12, dpi = 600, units = "in")
 ggsave("FINAL_CB_P1_wide_9_HD.jpg", plot = plot1, width = 5, height = 8, dpi = 600, units = "in")
```


```{r}
# merge 2 final aranged plots - this does NOT work well
plot9 = ggarrange(plot7, plot1, ncol = 2, nrow = 1)
# ggsave("CB_totalP_wide_1.jpg", plot = plot9, width = 10, height = 16, dpi = 300, units = "in")
# ggsave("CB_totalP_regular_1.jpg", plot = plot9, width = 10, height = 20, dpi = 300, units = "in")
# ggsave("CB_totalP_tall_1.jpg", plot = plot9, width = 10, height = 24, dpi = 300, units = "in")

plot9
```


# PLOT 2 
```{r}
rm(plot1, plot2, plot3, plot4, plot5, plot6, plot7)

load("E:/Masterarbeit/data/riskfactors_with_covariates_FINAL.rdata")
riskfactors_with_covariates_FINAL$class = as.factor(riskfactors_with_covariates_FINAL$class)
riskfactors_with_covariates_FINAL$class <- factor(riskfactors_with_covariates_FINAL$class, levels = c(3, 2, 1))

# NEW: remove stress
riskfactors_with_covariates_FINAL <- riskfactors_with_covariates_FINAL[riskfactors_with_covariates_FINAL$var != "STRESS", ]
```

## Overview Plot and Results
```{r}
plot1 = merge %>%
  mutate(class = factor(class)) %>%
  filter(!visit %in% c("3", "4")) %>%
  ggplot(aes(y = pgbi_p_ss_score, x = as.numeric(visit), color = class, fill = class)) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class)) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_color_manual(
    values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[5], '4' = viridis(10)[1]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[5], '4' = viridis(10)[1]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")
  ) +
  xlab("Visit") +
  ylab("Total score")+
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = "none"
  )+ 
   annotate("label", x = 0.75, y = 8, label = "High Symptoms", color = viridis(10)[10], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 0.75, y = 3.5, label = "Moderate Symptoms", color = viridis(10)[8], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 0.75, y = 1, label = "Low Symptoms", color = viridis(10)[5], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 0.75, y = 0.25, label = "No Symptoms", color = viridis(10)[1], fill = "white", size = 4, label.size = 0.5)
  



# Plot Odds Ratio.
plot2 = riskfactors_with_covariates_FINAL %>%    
  ggplot(aes(x=OR,y=reorder(var,OR)))+
  geom_vline(xintercept=1,linetype='dashed',linewidth=0.1)+
    geom_errorbar(aes(xmin=lower_95,xmax=upper_95,color=class),width=0,    linewidth=2.5,alpha=0.8,position=position_dodge(width=0.55))+
      geom_point(size=2.5,shape=21,fill="white",aes(color=class), position=position_dodge(width=0.55))+
         labs(x='Odds Ratio')+
            theme(axis.title.y = element_blank(),
              legend.position = "none",  # Removes the legend
              panel.grid = element_blank(),  # Removes gridlines
              legend.title = element_blank())+
                scale_color_manual(values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[5], '4' = viridis(10)[1]),
                     labels = c('1' = "High Symptoms VS. No Symptoms", 
                                '2' = "Moderate Symptoms VS. No Symptoms", 
                                '3' = "Low Symptoms VS. No Symptoms"),
                       limits = c('1', '2', '3')) +  # Change the order of the legend)
                      scale_y_discrete(labels=c("SLEEP" = "Sleep Disturbances",
      "IBS" = "Irritable bowel symptoms",
      "ASTHMA" = "Asthma",
      "BMI" = "BMI",
      "PREG" = "Pregnancy Complications",
      "OBST" = "Obstetric Complications",
      "PREMAT" = "Preterm birth",
      "SMALL" = "Small for gestational age",
      "CSECT" = "Cesarean birth",
      "DEPRESS" = "Depressive symptoms",
      "ANX" = "Anxiety symptoms",
      "ADHD" = "ADHD symptoms",
      "OPPOSIT" = "Oppositional defiant symptoms",
      "CONDUCT" = "Conduct disorder symptoms",
      "STRESS" = "Stress symptoms",
      "RAVLT" = "Verbal Memory",
      "FES_P" = "Family Conflict - Parent Rating",
      "FES_Y" = "Family Conflict - Youth Rating",
      "TRAUMA" = "Trauma",
      "MALTR" = "Maltreatment",
      "FIRST_D" = "Family history of mania"))



library(ggpubr)
plot3 = ggarrange(plot1, plot2, ncol = 2, nrow = 1, widths = c(1, 2) )
#plot4 = annotate_figure(plot3, left = textGrob("Total score", rot = 90, vjust = 1, gp = gpar(cex = 1)),
#                    bottom = textGrob("Visit", gp = gpar(cex = 1)))
# ggsave("CB_PL2_2_high.jpg", plot = plot3, width = 10, height = 6, dpi = 300, units = "in")
# ggsave("CB_PL2_2_normal.jpg", plot = plot3, width = 10, height = 5, dpi = 300, units = "in")
# ggsave("CB_PL2_2_wide.jpg", plot = plot3, width = 10, height = 4, dpi = 300, units = "in")

plot3
```

## Overview Plot and Results - Slightly Adjust Label (above line)
```{r}
plot1 = merge %>%
  mutate(class = factor(class)) %>%
  filter(!visit %in% c("3", "4")) %>%
  ggplot(aes(y = pgbi_p_ss_score, x = as.numeric(visit), color = class, fill = class)) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class)) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_color_manual(
    values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[5], '4' = viridis(10)[1]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[5], '4' = viridis(10)[1]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")
  ) +
  xlab("Visit") +
  ylab("Total score")+
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = "none"
  )+ 
   annotate("label", x = 0.75, y = 9.2, label = "High Symptoms", color = viridis(10)[10], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 0.75, y = 3.75, label = "Moderate Symptoms", color = viridis(10)[8], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 0.75, y = 1.3, label = "Low Symptoms", color = viridis(10)[5], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 0.75, y = 0.45, label = "No Symptoms", color = viridis(10)[1], fill = "white", size = 4, label.size = 0.5)
  



# Plot Odds Ratio.
plot2 = riskfactors_with_covariates_FINAL %>%    
  ggplot(aes(x=OR,y=reorder(var,OR)))+
  geom_vline(xintercept=1,linetype='dashed',linewidth=0.1)+
    geom_errorbar(aes(xmin=lower_95,xmax=upper_95,color=class),width=0,    linewidth=2.5,alpha=0.8,position=position_dodge(width=0.55))+
      geom_point(size=2.5,shape=21,fill="white",aes(color=class), position=position_dodge(width=0.55))+
         labs(x='Odds Ratio')+
            theme(axis.title.y = element_blank(),
              legend.position = "none",  # Removes the legend
              panel.grid = element_blank(),  # Removes gridlines
              legend.title = element_blank())+
                scale_color_manual(values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[5], '4' = viridis(10)[1]),
                     labels = c('1' = "High Symptoms VS. No Symptoms", 
                                '2' = "Moderate Symptoms VS. No Symptoms", 
                                '3' = "Low Symptoms VS. No Symptoms"),
                       limits = c('1', '2', '3')) +  # Change the order of the legend)
                      scale_y_discrete(labels=c("SLEEP" = "Sleep Disturbances",
      "IBS" = "Irritable bowel symptoms",
      "ASTHMA" = "Asthma",
      "BMI" = "BMI",
      "PREG" = "Pregnancy Complications",
      "OBST" = "Obstetric Complications",
      "PREMAT" = "Preterm birth",
      "SMALL" = "Small for gestational age",
      "CSECT" = "Cesarean birth",
      "DEPRESS" = "Depressive symptoms",
      "ANX" = "Anxiety symptoms",
      "ADHD" = "ADHD symptoms",
      "OPPOSIT" = "Oppositional defiant symptoms",
      "CONDUCT" = "Conduct disorder symptoms",
      "STRESS" = "Stress symptoms",
      "RAVLT" = "Verbal Memory",
      "FES_P" = "Family Conflict - Parent Rating",
      "FES_Y" = "Family Conflict - Youth Rating",
      "TRAUMA" = "Trauma",
      "MALTR" = "Maltreatment",
      "FIRST_D" = "Family history of mania"))



library(ggpubr)
plot3 = ggarrange(plot1, plot2, ncol = 2, nrow = 1, widths = c(1, 2) )
#plot4 = annotate_figure(plot3, left = textGrob("Total score", rot = 90, vjust = 1, gp = gpar(cex = 1)),
#                    bottom = textGrob("Visit", gp = gpar(cex = 1)))
# ggsave("CB_PL2_3_high.jpg", plot = plot3, width = 10, height = 6, dpi = 300, units = "in")
# ggsave("CB_PL2_3_normal.jpg", plot = plot3, width = 10, height = 5, dpi = 300, units = "in")
# ggsave("CB_PL2_3_wide.jpg", plot = plot3, width = 10, height = 4, dpi = 300, units = "in")

plot3
```

## Overview Plot and Results - Slightly Adjust Label (on top of line)
```{r}
plot1 = merge %>%
  mutate(class = factor(class)) %>%
  filter(!visit %in% c("3", "4")) %>%
  ggplot(aes(y = pgbi_p_ss_score, x = as.numeric(visit), color = class, fill = class)) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class)) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_color_manual(
    values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[5], '4' = viridis(10)[1]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[5], '4' = viridis(10)[1]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")
  ) +
  xlab("Visit") +
  ylab("Total score")+
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = "none"
  )+ 
   annotate("label", x = 0.75, y = 8.75, label = "High Symptoms", color = viridis(10)[10], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 0.75, y = 3.25, label = "Moderate Symptoms", color = viridis(10)[8], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 0.75, y = 0.88, label = "Low Symptoms", color = viridis(10)[5], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 0.75, y = 0.12, label = "No Symptoms", color = viridis(10)[1], fill = "white", size = 4, label.size = 0.5)
  



# Plot Odds Ratio.
plot2 = riskfactors_with_covariates_FINAL %>%    
  ggplot(aes(x=OR,y=reorder(var,OR)))+
  geom_vline(xintercept=1,linetype='dashed',linewidth=0.1)+
    geom_errorbar(aes(xmin=lower_95,xmax=upper_95,color=class),width=0,    linewidth=2.5,alpha=0.8,position=position_dodge(width=0.55))+
      geom_point(size=2.5,shape=21,fill="white",aes(color=class), position=position_dodge(width=0.55))+
         labs(x='Odds Ratio')+
            theme(axis.title.y = element_blank(),
              legend.position = "none",  # Removes the legend
              panel.grid = element_blank(),  # Removes gridlines
              legend.title = element_blank())+
                scale_color_manual(values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[5], '4' = viridis(10)[1]),
                     labels = c('1' = "High Symptoms VS. No Symptoms", 
                                '2' = "Moderate Symptoms VS. No Symptoms", 
                                '3' = "Low Symptoms VS. No Symptoms"),
                       limits = c('1', '2', '3')) +  # Change the order of the legend)
                      scale_y_discrete(labels=c("SLEEP" = "Sleep Disturbances",
      "IBS" = "Irritable bowel symptoms",
      "ASTHMA" = "Asthma",
      "BMI" = "BMI",
      "PREG" = "Pregnancy Complications",
      "OBST" = "Obstetric Complications",
      "PREMAT" = "Preterm birth",
      "SMALL" = "Small for gestational age",
      "CSECT" = "Cesarean birth",
      "DEPRESS" = "Depressive symptoms",
      "ANX" = "Anxiety symptoms",
      "ADHD" = "ADHD symptoms",
      "OPPOSIT" = "Oppositional defiant symptoms",
      "CONDUCT" = "Conduct disorder symptoms",
      "STRESS" = "Stress symptoms",
      "RAVLT" = "Verbal Learning",
      "FES_P" = "Family Conflict - Parent Rating",
      "FES_Y" = "Family Conflict - Youth Rating",
      "TRAUMA" = "Trauma",
      "MALTR" = "Maltreatment",
      "FIRST_D" = "Family history of mania"))



library(ggpubr)
plot3 = ggarrange(plot1, plot2, ncol = 2, nrow = 1, widths = c(1, 2) )
#plot4 = annotate_figure(plot3, left = textGrob("Total score", rot = 90, vjust = 1, gp = gpar(cex = 1)),
#                    bottom = textGrob("Visit", gp = gpar(cex = 1)))
# ggsave("N_PL2_1_high.jpg", plot = plot3, width = 10, height = 6, dpi = 300, units = "in")
# ggsave("N_PL2_1_normal.jpg", plot = plot3, width = 10, height = 5, dpi = 300, units = "in")
# ggsave("N_PL2_1_wide.jpg", plot = plot3, width = 10, height = 4, dpi = 300, units = "in")

plot3
```




## FINAL PLOT2 Overview Plot and Results - Slightly Adjust Label (on top of line; switched color)
```{r}
plot1 = merge %>%
  mutate(class = factor(class)) %>%
  filter(!visit %in% c("3", "4")) %>%
  ggplot(aes(y = pgbi_p_ss_score, x = as.numeric(visit), color = class, fill = class)) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class)) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_color_manual(
    values = c('1' = viridis(10)[1], '2' = viridis(10)[4], '3' = viridis(10)[8], '4' = viridis(10)[10]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[1], '2' = viridis(10)[4], '3' = viridis(10)[8], '4' = viridis(10)[10]),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")
  ) +
  xlab("Visit") +
  ylab("Total score")+
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = "none"
  )+ 
   annotate("label", x = 0.75, y = 8.75, label = "High Symptoms", color = viridis(10)[1], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 0.75, y = 3.25, label = "Moderate Symptoms", color = viridis(10)[4], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 0.75, y = 0.88, label = "Low Symptoms", color = viridis(10)[8], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 0.75, y = 0.12, label = "No Symptoms", color = viridis(10)[10], fill = "white", size = 4, label.size = 0.5)
  



# Plot Odds Ratio.
plot2 = riskfactors_with_covariates_FINAL %>%    
  ggplot(aes(x=OR,y=reorder(var,OR)))+
  geom_vline(xintercept=1,linetype='dashed',linewidth=0.1)+
    geom_errorbar(aes(xmin=lower_95,xmax=upper_95,color=class),width=0,    linewidth=2.5,alpha=0.8,position=position_dodge(width=0.55))+
      geom_point(size=2.5,shape=21,fill="white",aes(color=class), position=position_dodge(width=0.55))+
         labs(x='Odds Ratio')+
            theme(axis.title.y = element_blank(),
              legend.position = "none",  # Removes the legend
              panel.grid = element_blank(),  # Removes gridlines
              legend.title = element_blank())+
                scale_color_manual(values = c('1' = viridis(10)[1], '2' = viridis(10)[4], '3' = viridis(10)[8], '4' = viridis(10)[10]),
                     labels = c('1' = "High Symptoms VS. No Symptoms", 
                                '2' = "Moderate Symptoms VS. No Symptoms", 
                                '3' = "Low Symptoms VS. No Symptoms"),
                       limits = c('1', '2', '3')) +  # Change the order of the legend)
                      scale_y_discrete(labels=c("SLEEP" = "Sleep Disturbances",
      "IBS" = "Irritable bowel symptoms",
      "ASTHMA" = "Asthma",
      "BMI" = "BMI",
      "PREG" = "Pregnancy Complications",
      "OBST" = "Obstetric Complications",
      "PREMAT" = "Preterm birth",
      "SMALL" = "Small for gestational age",
      "CSECT" = "Cesarean birth",
      "DEPRESS" = "Depressive symptoms",
      "ANX" = "Anxiety symptoms",
      "ADHD" = "ADHD symptoms",
      "OPPOSIT" = "Oppositional defiant symptoms",
      "CONDUCT" = "Conduct disorder symptoms",
      "STRESS" = "Stress symptoms",
      "RAVLT" = "Verbal Memory",
      "FES_P" = "Family Conflict - Parent Rating",
      "FES_Y" = "Family Conflict - Youth Rating",
      "TRAUMA" = "Trauma",
      "MALTR" = "Maltreatment",
      "FIRST_D" = "Family history of mania"))



library(ggpubr)
plot3 = ggarrange(plot1, plot2, ncol = 2, nrow = 1, widths = c(1, 2) )
#plot4 = annotate_figure(plot3, left = textGrob("Total score", rot = 90, vjust = 1, gp = gpar(cex = 1)),
#                    bottom = textGrob("Visit", gp = gpar(cex = 1)))
# ggsave("CB_PL2_5_high3.jpg", plot = plot3, width = 10, height = 8, dpi = 300, units = "in")
# ggsave("CB_PL2_5_high2.jpg", plot = plot3, width = 10, height = 7, dpi = 300, units = "in")
# ggsave("CB_PL2_5_high.jpg", plot = plot3, width = 10, height = 6, dpi = 300, units = "in")
# ggsave("CB_PL2_5_normal.jpg", plot = plot3, width = 10, height = 5, dpi = 300, units = "in")
# ggsave("CB_PL2_5_wide.jpg", plot = plot3, width = 10, height = 4, dpi = 300, units = "in")

plot3

```

## FINAL PLOT2 super tall plot; switched color - OLD
```{r}
plot1 = merge %>%
  mutate(class = factor(class)) %>%
  filter(!visit %in% c("3", "4")) %>%
  ggplot(aes(y = pgbi_p_ss_score, x = as.numeric(visit), color = class, fill = class)) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class)) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_color_manual(
    values = c('1' = viridis(10)[1], '2' = viridis(10)[4], '3' = viridis(10)[8], '4' = "gold2"),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[1], '2' = viridis(10)[4], '3' = viridis(10)[8], '4' = "gold2"),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")
  ) +
  xlab("Visit") +
  ylab("Total score")+
  theme(
  panel.grid = element_blank(),  # Remove gridlines
  panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
  legend.position = "none"
  )+ 
   annotate("label", x = 0.75, y = 8.75, label = "High Symptoms", color = viridis(10)[1], fill = "white", size =3, label.size = 0.5) +
  annotate("label", x = 0.75, y = 3.25, label = "Moderate Symptoms", color = viridis(10)[4], fill = "white", size = 3, label.size = 0.5) +
  annotate("label", x = 0.75, y = 0.88, label = "Low Symptoms", color = viridis(10)[8], fill = "white", size = 3, label.size = 0.5) +
  annotate("label", x = 0.75, y = 0.12, label = "No Symptoms", color = "gold2", fill = "white", size = 3, label.size = 0.5)

# Plot Odds Ratio.
plot2 = riskfactors_with_covariates_FINAL %>%    
  ggplot(aes(x=OR,y=reorder(var,OR)))+
  geom_vline(xintercept=1,linetype='dashed',linewidth=0.1)+
    geom_errorbar(aes(xmin=lower_95,xmax=upper_95,color=class),width=0,    linewidth=2.5,alpha=0.8,position=position_dodge(width=0.55))+
      geom_point(size=2.5,shape=21,fill="white",aes(color=class), position=position_dodge(width=0.55))+
         labs(x='Odds Ratio')+
            theme(axis.title.y = element_blank(),
              legend.position = "none",  # Removes the legend
              panel.grid = element_blank(),  # Removes gridlines
              legend.title = element_blank())+
                scale_color_manual(values = c('1' = viridis(10)[1], '2' = viridis(10)[4], '3' = viridis(10)[8], '4' = viridis(10)[10]),
                     labels = c('1' = "High Symptoms VS. No Symptoms", 
                                '2' = "Moderate Symptoms VS. No Symptoms", 
                                '3' = "Low Symptoms VS. No Symptoms"),
                       limits = c('1', '2', '3')) +  # Change the order of the legend)
                      scale_y_discrete(labels=c("SLEEP" = "Sleep Disturbances",
      "IBS" = "Irritable bowel symptoms",
      "ASTHMA" = "Asthma",
      "BMI" = "BMI",
      "PREG" = "Pregnancy Complications",
      "OBST" = "Obstetric Complications",
      "PREMAT" = "Preterm birth",
      "SMALL" = "Small for gestational age",
      "CSECT" = "Cesarean birth",
      "DEPRESS" = "Depressive symptoms",
      "ANX" = "Anxiety symptoms",
      "ADHD" = "ADHD symptoms",
      "OPPOSIT" = "Oppositional defiant symptoms",
      "CONDUCT" = "Conduct disorder symptoms",
      "STRESS" = "Stress symptoms",
      "RAVLT" = "Verbal Learning",
      "FES_P" = "Family Conflict - Parent Rating",
      "FES_Y" = "Family Conflict - Youth Rating",
      "TRAUMA" = "Trauma",
      "MALTR" = "Maltreatment",
      "FIRST_D" = "Family history of mania"))
```

## FINAL PLOT2 super tall plot; switched color - UPDATED
```{r}
# new code for bigger labels
plot1 = merge %>%
  mutate(class = factor(class)) %>%
  filter(!visit %in% c("3", "4")) %>%
  ggplot(aes(y = pgbi_p_ss_score, x = as.numeric(visit), color = class, fill = class)) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), aes(group = class)) +
  scale_x_continuous(breaks = scales::breaks_width(1)) +
  scale_color_manual(
    values = c('1' = viridis(10)[1], '2' = viridis(10)[4], '3' = viridis(10)[8], '4' = "gold2"),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")
  ) +
  scale_fill_manual(
    values = c('1' = viridis(10)[1], '2' = viridis(10)[4], '3' = viridis(10)[8], '4' = "gold2"),
    labels = c('1' = "High", '2' = "Moderate", '3' = "Low", '4' = "None")
  ) +
  xlab("Visit") +
  ylab("Total Score") +
  theme(
    panel.grid = element_blank(),  # Remove gridlines
    panel.border = element_rect(color = "black", fill = NA),  # Add the outline back
    legend.position = "none",
    axis.text.x = element_text(size = 14),  # Increase x-axis text size
    axis.text.y = element_text(size = 14),  # Increase y-axis text size
    axis.title.x = element_text(size = 16, face = "bold"),  # Increase x-axis title size
    axis.title.y = element_text(size = 16, face = "bold")   # Increase y-axis title size
  ) +
  annotate("label", x = 1, y = 8.75, label = "High Symptoms", color = viridis(10)[1], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 1, y = 3.25, label = "Moderate Symptoms", color = viridis(10)[4], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 1, y = 0.88, label = "Low Symptoms", color = viridis(10)[8], fill = "white", size = 4, label.size = 0.5) +
  annotate("label", x = 1, y = 0.12, label = "No Symptoms", color = "gold2", fill = "white", size = 4, label.size = 0.5)

# new code for bigger labels
plot2 = riskfactors_with_covariates_FINAL %>%    
  ggplot(aes(x=OR,y=reorder(var,OR)))+
  geom_vline(xintercept=1,linetype='dashed',linewidth=0.1)+
    geom_errorbar(aes(xmin=lower_95,xmax=upper_95,color=class),width=0,linewidth=2.5,alpha=0.8,position=position_dodge(width=0.55))+
      geom_point(size=2.5,shape=21,fill="white",aes(color=class), position=position_dodge(width=0.55))+
         labs(x='Odds Ratio')+
         theme(
           axis.title.y = element_blank(),
           axis.text.y = element_text(size = 14),  # Increased label size
           axis.title.x = element_text(size = 16, face = "bold"),  # Larger x-axis title
           legend.position = "none",  # Removes the legend
           panel.grid = element_blank(),  # Removes gridlines
           legend.title = element_blank()
         )+
         scale_color_manual(values = c('1' = viridis(10)[1], '2' = viridis(10)[4], '3' = viridis(10)[8], '4' = viridis(10)[10]),
             labels = c('1' = "High Symptoms VS. No Symptoms", 
                        '2' = "Moderate Symptoms VS. No Symptoms", 
                        '3' = "Low Symptoms VS. No Symptoms"),
             limits = c('1', '2', '3')) +  # Change the order of the legend
         scale_y_discrete(labels = c(
           "SLEEP" = "Sleep Disturbances",
           "IBS" = "Irritable Bowel Symptoms",
           "ASTHMA" = "Asthma",
           "BMI" = "BMI",
           "PREG" = "Pregnancy Complications",
           "OBST" = "Obstetric Complications",
           "PREMAT" = "Preterm Birth",
           "SMALL" = "Small for Gestational Age",
           "CSECT" = "Cesarean Birth",
           "DEPRESS" = "Depressive Symptoms",
           "ANX" = "Anxiety Symptoms",
           "ADHD" = "ADHD Symptoms",
           "OPPOSIT" = "Oppositional Defiant Symptoms",
           "CONDUCT" = "Conduct Disorder Symptoms",
           "STRESS" = "Stress Symptoms",
           "RAVLT" = "Verbal Learning",
           "FES_P" = "Family Conflict - Parent Rating",
           "FES_Y" = "Family Conflict - Youth Rating",
           "TRAUMA" = "Trauma",
           "MALTR" = "Maltreatment",
           "FIRST_D" = "Family History of Mania"
         ))

plot3 = ggarrange(plot1, plot2, ncol = 2, nrow = 1, widths = c(1, 3) )
 ggsave("NS_N_PL2_1_high.jpg", plot = plot3, width = 12, height = 7, dpi = 600, units = "in")
 ggsave("NS_N_PL2_1_medium.jpg", plot = plot3, width = 13, height = 7, dpi = 600, units = "in")
 ggsave("NS_N_PL2_1_tall.jpg", plot = plot3, width = 14, height = 7, dpi = 600, units = "in")

plot3
```

# PLOT3 (Supplement)
```{r}
rm(plot1, plot2, plot3, riskfactors_with_covariates_FINAL)
load("D:/Masterarbeit/data/riskfactors_sleep_FINAL.rdata")
```

### without gridlines
```{r}
riskfactors_sleep_FINAL$class <- factor(riskfactors_sleep_FINAL$class, levels = c(3, 2, 1))

# Plot Odds Ratio
plot = riskfactors_sleep_FINAL %>%    
ggplot(aes(x=OR,y=reorder(var,OR)))+
  geom_vline(xintercept=1,linetype='dashed',linewidth=0.1)+
    geom_errorbar(aes(xmin=lower_95,xmax=upper_95,color=class),width=0, linewidth=2.5,alpha=0.8,position=position_dodge(width=0.55))+
      geom_point(size=2.5,shape=21,fill="white",aes(color=class), position=position_dodge(width=0.55))+
         labs(x='Odds Ratio')+
            theme(axis.title.y = element_blank(),
              panel.grid = element_blank(),  # Removes gridlines
              legend.title = element_blank())+
                scale_color_manual(values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[5]),
                     labels = c('3' = "Low Symptoms", 
                                '2' = "Moderate Symptoms", 
                                '1' = "High Symptoms"),
                       limits = c('3', '2', '1')) +  # Change the order of the legend)
                        theme(legend.position = "bottom")+
scale_y_discrete(labels=c("DIMS" = "Disorders of initiating and maintaining sleep", "SBD" = "Sleep breathing disorders", "DA" = "Disorders of arousal", "SWTD" = "Sleep-wake transition disorders", "DOES" = "Disorders of excessive somnolence", "SHY" = "Sleep hyperhydrosis"))

# ggsave("CB_sleep_blank_tall.jpg", plot = plot, width = 10, height = 5, dpi = 300, units = "in")
# ggsave("CB_sleep_blank_regular.jpg", plot = plot, width = 10, height = 4, dpi = 300, units = "in")
# ggsave("CB_sleep_blank_wide.jpg", plot = plot, width = 10, height = 3.5, dpi = 300, units = "in")

plot
```

### with grid
```{r}
riskfactors_sleep_FINAL$class <- factor(riskfactors_sleep_FINAL$class, levels = c(3, 2, 1))

# Plot Odds Ratio
plot = riskfactors_sleep_FINAL %>%    
ggplot(aes(x=OR,y=reorder(var,OR)))+
  geom_vline(xintercept=1,linetype='dashed',linewidth=0.1)+
    geom_errorbar(aes(xmin=lower_95,xmax=upper_95,color=class),width=0, linewidth=2.5,alpha=0.8,position=position_dodge(width=0.55))+
      geom_point(size=2.5,shape=21,fill="white",aes(color=class), position=position_dodge(width=0.55))+
         labs(x='Odds Ratio')+
            theme(axis.title.y = element_blank(),
                legend.title = element_blank())+
                scale_color_manual(values = c('1' = viridis(10)[10], '2' = viridis(10)[8], '3' = viridis(10)[5]),
                     labels = c('3' = "Low Symptoms", 
                                '2' = "Moderate Symptoms", 
                                '1' = "High Symptoms"),
                       limits = c('3', '2', '1')) +  # Change the order of the legend)
                        scale_x_continuous(breaks = seq(0.5, 3.0, by = 0.5), limits = c(0.75, 3.0))+
                        theme(legend.position = "bottom")+
scale_y_discrete(labels=c("DIMS" = "Disorders of initiating and maintaining sleep", "SBD" = "Sleep breathing disorders", "DA" = "Disorders of arousal", "SWTD" = "Sleep-wake transition disorders", "DOES" = "Disorders of excessive somnolence", "SHY" = "Sleep hyperhydrosis"))

# ggsave("CB_sleep_grid_tall.jpg", plot = plot, width = 10, height = 5, dpi = 300, units = "in")
# ggsave("CB_sleep_grid_regular.jpg", plot = plot, width = 10, height = 4, dpi = 300, units = "in")
# ggsave("CB_sleep_grid_wide.jpg", plot = plot, width = 10, height = 3.5, dpi = 300, units = "in")

plot
```

### without gridlines; switched colors
```{r}
riskfactors_sleep_FINAL$class <- factor(riskfactors_sleep_FINAL$class, levels = c(3, 2, 1))

# Plot Odds Ratio
plot = riskfactors_sleep_FINAL %>%    
ggplot(aes(x=OR,y=reorder(var,OR)))+
  geom_vline(xintercept=1,linetype='dashed',linewidth=0.1)+
    geom_errorbar(aes(xmin=lower_95,xmax=upper_95,color=class),width=0, linewidth=2.5,alpha=0.8,position=position_dodge(width=0.55))+
      geom_point(size=2.5,shape=21,fill="white",aes(color=class), position=position_dodge(width=0.55))+
         labs(x='Odds Ratio')+
            theme(axis.title.y = element_blank(),
              panel.grid = element_blank(),  # Removes gridlines
              legend.title = element_blank())+
                scale_color_manual(values = c('1' = viridis(10)[1], '2' = viridis(10)[4], '3' = viridis(10)[8]),
                     labels = c('3' = "Low Symptoms", 
                                '2' = "Moderate Symptoms", 
                                '1' = "High Symptoms"),
                       limits = c('3', '2', '1')) +  # Change the order of the legend)
                        theme(legend.position = "bottom")+
scale_y_discrete(labels=c("DIMS" = "Disorders of initiating and maintaining sleep", "SBD" = "Sleep breathing disorders", "DA" = "Disorders of arousal", "SWTD" = "Sleep-wake transition disorders", "DOES" = "Disorders of excessive somnolence", "SHY" = "Sleep hyperhydrosis"))

# ggsave("CB_sleep_blank_1_tall.jpg", plot = plot, width = 10, height = 5, dpi = 300, units = "in")
# ggsave("CB_sleep_blank_1_regular.jpg", plot = plot, width = 10, height = 4, dpi = 300, units = "in")
# ggsave("CB_sleep_blank_1_wide.jpg", plot = plot, width = 10, height = 3.5, dpi = 300, units = "in")

plot
```